### 2017-04-05 Project_Abstract.Rmd
Added Project_Abstract.Rmd file to repository

---
title: "Interactive Weather Chart"
author: "Katie Will, Kiegan Rice"
date: "4/4/2017"
output: pdf_document
---

### Abstract

In 2016, the New York Times published an interactive chart displaying 2015 temperature data for 3,116 U.S. cities. We plan on scraping historical data from *Weather Underground* for multiple cities for the years of 1945-2017. With this data, we plan on recreating the interactive chart published by the New York Times using a Shiney applet. Our chart, however, will have an extra feature that takes into accout the year. With our visual, we will display the daily temperature averages as well as the record highs and lows.

### 2017-04-05 Project_Abstract.Rmd
Added Amy to Authors
Make "weather underground" a url link

@@
 title: "Interactive Weather Chart"
-author: "Katie Will, Kiegan Rice"
+author: "Katie Will, Kiegan Rice, Amy Crawford"
 date: "4/4/2017"
@@
 cities.
-We plan on scraping historical data from *Weather Underground* for multiple cities for the years of 1945-2017.
+We plan on scraping historical data from [Weather Underground](https://www.wunderground.com/) for multiple cities for the years of 1945-2017.
 With this data, we plan on recreating the interactive chart published by the New York Times using a Shiney applet.

### 2017-04-05 Project_Abstract.Rmd
abstract change and Rproj

--- 2017-04-05 Project_Abstract.Rmd
@@
 
-In 2016, the New York Times published an interactive chart displaying 2015 temperature data for 3,116 U.S.
-cities.
-We plan on scraping historical data from *Weather Underground* for multiple cities for the years of 1945-2017.
-With this data, we plan on recreating the interactive chart published by the New York Times using a Shiney applet.
-Our chart, however, will have an extra feature that takes into accout the year.
-With our visual, we will display the daily temperature averages as well as the record highs and lows.
+The New York Times' mapping of weather data for a year, published originally in 1979 and changed in several ways over the years, is a classic visualization of temperature trends and how the temperatures in a year compare to historic averages and records.
+In 2016, the New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
+In this project, we scrape historical data from *Weather Underground* for multiple cities for the years 1945 to 2017.
+With this data, we recreate the interactive chart published by the New York Times and allow for user interaction via a shiny app.
+Although we do not include all 3,116 cities, our app includes extra features that allow for users to view the data over many years and choose the features they want included on their version of this iconic chart.

### 2017-04-05 Project_Abstract.Rmd
update
Re-change "weather underground" to a url link

@@
 In 2016, the New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
-In this project, we scrape historical data from *Weather Underground* for multiple cities for the years 1945 to 2017.
+In this project, we scrape historical data from [Weather Underground](https://www.wunderground.com/) for multiple cities for the years 1945 to 2017.
 With this data, we recreate the interactive chart published by the New York Times and allow for user interaction via a shiny app.

### 2017-04-05 Project_Abstract.Rmd
bye bye date
Update Project_Abstract.Rmd

@@
 author: "Katie Will, Kiegan Rice, Amy Crawford"
-date: "4/4/2017"
 output: pdf_document
@@
 
-The New York Times' mapping of weather data for a year, published originally in 1979 and changed in several ways over the years, is a classic visualization of temperature trends and how the temperatures in a year compare to historic averages and records.
-In 2016, the New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
+In 1979 the New York Times' published what would become a classic visualization of weather data that maps how temperatures compare to historic averages and records over the course of one year.
+This visualization has changed in several ways over the years, and in 2016....
+
+_The New York Times' mapping of weather data for a year, published originally in 1979 and changed in several ways over the years, is a classic visualization of temperature trends and how the temperatures in a year compare to historic averages and records.
+In 2016,_ the New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
 In this project, we scrape historical data from [Weather Underground](https://www.wunderground.com/) for multiple cities for the years 1945 to 2017.

### 2017-04-05 Project_Abstract.Rmd
Replaced first sentence

--- 2017-04-05 Project_Abstract.Rmd
@@
 
-The New York Times' mapping of weather data for a year, published originally in 1979 and changed in several ways over the years, is a classic visualization of temperature trends and how the temperatures in a year compare to historic averages and records.
-In 2016, the New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
+In 1979 The New York Times' published what would become a classic visualization of weather data that maps how temperatures compare to historic averages and records over the course of one year.
+This visualization has changed in several ways over the years, and in 2016 The New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.
 In this project, we scrape historical data from [Weather Underground](https://www.wunderground.com/) for multiple cities for the years 1945 to 2017.
-With this data, we recreate the interactive chart published by the New York Times and allow for user interaction via a shiny app.
+With this data, we recreate the interactive chart published by The New York Times and allow for user interaction via a shiny app.
 Although we do not include all 3,116 cities, our app includes extra features that allow for users to view the data over many years and choose the features they want included on their version of this iconic chart.

### 2017-04-05 Project_Abstract.Rmd
Update Project_Abstract.Rmd

@@
 With this data, we recreate the interactive chart published by The New York Times and allow for user interaction via a shiny app.
-Although we do not include all 3,116 cities, our app includes extra features that allow for users to view the data over many years and choose the features they want included on their version of this iconic chart.
+Although we do not include all 3,116 cities, our app includes extra features that allow for users to view the data over the course of many years and choose the features they would like to include on their version of this iconic chart.

### 2017-04-05 Project_Abstract.Rmd
Update Project_Abstract.Rmd
Title
Removed apostrophe

@@
 ---
-title: "Interactive Weather Chart"
+title: "A (sun)Shiny Recreation of the New York Times Weather Chart"
 author: "Katie Will, Kiegan Rice, Amy Crawford"
@@
 
-In 1979 The New York Times' published what would become a classic visualization of weather data that maps how temperatures compare to historic averages and records over the course of one year.
+In 1979 The New York Times published what would become a classic visualization of weather data that maps how temperatures compare to historic averages and records over the course of one year.
 This visualization has changed in several ways over the years, and in 2016 The New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities.

### 2017-04-08 Web_Scraping.Rmd
Add files via upload

---
title: 'Sun Shiny Weather: Web Scraping'
output: html_document
---

Reading in required packages:
```{r, include = F, warning = F, message = F}
library(tidyverse)
library(rvest)
library(lubridate)
```

Currently only for Des Moines airport, which starts 1945-01-01 with both 'actual' and 'average' temps.
Some airports don't have 'actual' temps until a later date.

Extracting temps for each days and record temps in one loop. (this is redundant) This will also take a couple hours to run. 
```{r, include = F, warning = F, message = F}
Date <- ymd("1945-01-01")  # set a starting date
day_temps <- list()        # empty list for min, max, and mean temps, actual and historical averages
record_temps <- list()     # empty list for record temps
                           # one item in the list for each day
i <- 1                     # counter for the list item

# Need to create the url which changes for each day (and each airport)
url_begin <- "https://www.wunderground.com/history/airport/" 
airport <- "KDSM/"                  # This will change in loop (eventually)
url_end <- "/DailyHistory.html"

  while(Date < Sys.Date()){
    date <- gsub("-", "/", Date)      
    url <- paste(url_begin, airport, date, url_end, sep = "") # Pasting together parts of url
    html <- read_html(url)

    # grabbing the "Actual" daily temperatures (mean, min, and max)
    actual_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text %>% 
      gsub("-", "NA", .) %>% gsub("°F", "", .) %>% gsub("\n", "", .) %>% gsub("[[:blank:]]", "", .)

    # grabbing the historical "Average" temperatures (mean, min, and max)
    average_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text %>% 
      gsub("-", "NA", .) %>% gsub("°F", "", .) %>% gsub("\n", "", .) %>% gsub("[[:blank:]]", "", .)

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    # grabbing the record min and max for each day
    # this is redundant and may need to be fixed for efficiency purposes
    record <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(4) , #historyTable tr:nth-child(3) td:nth-child(4)") %>%
      html_text()
    record_vals <- parse_number(record)
    record_yrs <- record %>% gsub("^[^\\(]+", "", .) %>% parse_number(.)

    # putting data into a data frame which then makes up one item in the master list
    # two different lists (one for daily temps and one for the record temps)
    day_temps[[i]] <- data.frame(day = Date,
                          mean_max_min = rep(temp, times = 2),
                          actual_ave = rep(c("Actual", "Historical Average"), each = 3),
                          value = as.numeric(c(actual_vals, average_vals)))

    record_temps[[i]] <- data.frame(day = "08-11",
                               year = record_yrs,
                               record_type = c("Max", "Min"),
                               value = record_vals)

    Date <- Date+1
    i <- i+1
  }

# binding together all items of the list
DSM_temps <- dplyr::bind_rows(day_temps)
DSM_records <- dplyr::bind_rows(record_temps)
```

To fix the redundancy, split the loop into two.

This loop extracts the record temps (so a min and max for 366 days)
```{r}
# Two while loops to fix the redundant records

# loop to grab record min and max from the web (note this is only for 366 days)
Date <- ymd("2016-01-01")
record_temps <- list() 
i <- 1

# Need to create the url which changes for each day (and each airport)
url_begin <- "https://www.wunderground.com/history/airport/" 
airport <- "KDSM/"                  # This will change in loop (eventually)
url_end <- "/DailyHistory.html"

  while(Date < ymd("2017-01-01")){
    date <- gsub("-", "/", Date)      
    url <- paste(url_begin, airport, date, url_end, sep = "") # Pasting together parts of url
    html <- read_html(url)

    # grabbing the record min and max for each day
    # this is redundant and may need to be fixed for efficiency purposes
    record <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(4) , #historyTable tr:nth-child(3) td:nth-child(4)") %>%
      html_text()
    record_vals <- parse_number(record)
    record_yrs <- record %>% gsub("^[^\\(]+", "", .) %>% parse_number(.)

    record_temps[[i]] <- data.frame(month_number = month(Date, label = F),
                                    month_name = month(Date, label = T),
                                    day = day(Date),
                                    record_year = record_yrs,
                                    record_type = c("Max", "Min"),
                                    value = record_vals)

    Date <- Date+1
    i <- i+1
  }

DSM_records <- dplyr::bind_rows(record_temps)

```

Plots of record temps
```{r}
DSM_records <- DSM_records %>% mutate(day_of_year = 1:nrow(DSM_records), date = as.Date(paste(month_name, day, sep = "-"), format = "%b-%d"))

plot1 <-  DSM_records %>% ggplot(aes(y = value, x = day_of_year, colour = record_type)) +
                            geom_point(aes(text = record_year))
plotly::ggplotly(plot1)

plot1 <-  DSM_records %>% ggplot(aes(y = value, x = month_number, colour = record_type)) + 
                            geom_point(aes(text = record_year)) +
                            scale_x_discrete(name = "Month", 
                                             breaks = data$month_number,
                                             labels = data$month_name
                                             )

```

This loop extracts the temps for each day (so a min, max, mean for 'actual' and 'average' for approx. 26,280 days)
```{r}
# loop to grab daily temps from the web (note this is approximately 26,000 days for DSM)
Date <- ymd("1945-01-01")  # set a starting date
day_temps <- list()        # empty list for min, max, and mean temps, actual and historical averages
i <- 1                     # counter for the list item

# Need to create the url which changes for each day (and each airport)
url_begin <- "https://www.wunderground.com/history/airport/" 
airport <- "KDSM/"                  # This will change in loop (eventually)
url_end <- "/DailyHistory.html"

  while(Date < Sys.Date()){
    date <- gsub("-", "/", Date)      
    url <- paste(url_begin, airport, date, url_end, sep = "") # Pasting together parts of url
    html <- read_html(url)

    # grabbing the "Actual" daily temperatures (mean, min, and max)
    actual_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text %>% 
      gsub("-", "NA", .) %>% gsub("°F", "", .) %>% gsub("\n", "", .) %>% gsub("[[:blank:]]", "", .)

    # grabbing the historical "Average" temperatures (mean, min, and max)
    average_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text %>% 
      gsub("-", "NA", .) %>% gsub("°F", "", .) %>% gsub("\n", "", .) %>% gsub("[[:blank:]]", "", .)

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    # putting data into a data frame which then makes up one item in the master list
    # two different lists (one for daily temps and one for the record temps)
    day_temps[[i]] <- data.frame(year = year(Date), 
                                 month = month(Date, label = T),
                                 day = day(Date),
                                 mean_max_min = rep(temp, times = 2),
                                 actual_ave = rep(c("Actual", "Historical Average"), each = 3),
                                 value = as.numeric(c(actual_vals, average_vals)))

    Date <- Date+1
    i <- i+1
  }

DSM_temps <- dplyr::bind_rows(day_temps)

```

*Attempt to optimize:* 
```{r}
library(reshape)
# Attempt at better efficiency... using html_table

Date <- ymd("1945-01-01")

# URL code stays the same
    url_begin <- "https://www.wunderground.com/history/airport/" 
    airport <- "KDSM/"                  # This will change in loop (eventually)
    date <- gsub("-", "/", Date)      
    url_end <- "/DailyHistory.html"
    url <- paste(url_begin, airport, date, url_end, sep = "") # Pasting together parts of url
    html <- read_html(url)
    tables <- html %>% html_table(fill = TRUE)

    sm_table <- tables[[1]][2:4,1:3]
    sm_table <- setNames(sm_table, c("Temperature", "Actual", "Average"))
    rec_table <- tables[[1]][3:4, c(1,4)] 
    rec_table <- rec_table %>% setNames(., c("Temperature", "Record")) %>%
                      transform(., Record = colsplit(Record, split = "\\\n", names = c('temp', 'year')))
    sm_table
    rec_table

```

### 2017-04-08 shiny/app.R
shiny folder

@@ -1,0 +1,38 @@
+library(shiny)
+require(ggplot2)
+require(dplyr)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(    
+  # Application title
+  titlePanel("Hello Shiny World!"),
+  
+  # Sidebar with a slider input for the number of bins
+  sidebarPanel(
+    sliderInput("num",
+                "Number of Samples:",
+                min = 1,
+                max = 5000,
+                value = 2500)
+  ),
+  
+  # Show a plot of the generated distribution
+  mainPanel(
+    plotOutput("hist")
+  )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+  output$hist <- renderPlot({
+    dist <- rnorm(n = input$num)
+    gg <- data.frame(dist) %>% 
+      ggplot(aes(x = dist)) + geom_histogram(binwidth = 0.25) +
+      xlim(c(-10,10))
+    print(gg)
+  })
+}
+
+# Bind ui and server together
+shinyApp(ui, server)
+

### 2017-04-08 Web_Scraping_attempt2.Rmd
Add files via upload

---
title: 'Web Scraping: attempt 2'
author: "Katie Will"
date: "April 8, 2017"
output: html_document
---

*html_session within function *

4/8/17  1:44pm    SYSTEM.TIME:  336.107 seconds elapsed

```{r}
#url_begin <- "https://www.wunderground.com/history/airport/KDSM/" 
link_dates <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), to = Sys.Date(), by = "days"))
links <- paste0(link_dates, "/DailyHistory.html?req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo=")

#date <- "2017/04/08"
#links <- paste0(date, "/DailyHistory.html?req_city=&req_state=&req_statename=&reqdb.zip=&reqdb.magic=&reqdb.wmo=")

#s <- html_session("https://www.wunderground.com/history/airport/")
#html_form(s)

grab_temps <- function(link){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KDSM/",link))
  html <- read_html(ss)

  actual_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the historical "Average" temperatures (mean, min, and max)
  average_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
                      mean_max_min = as.character(rep(temp, times = 2)),
                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
                      value = as.numeric(c(actual_vals, average_vals))))
}

## WORKING ###
df2 <- data.frame(Links = links[1:365])
system.time(df2 %>% nest() %>% mutate(daily_temps = Links %>% purrr::map(grab_temps))) #%>% select(-Links) %>% unnest()
##############

```

*Pasting togeter url and then using read_html*

4/8/17  1:52pm   SYSTEM.TIME:   343.802 elapsed

```{r}

grab_temps2 <- function(date){
    url <- paste0("https://www.wunderground.com/history/airport/", "KDSM/", date, "/DailyHistory.html") # Pasting together parts of url
    html <- read_html(url)

  actual_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the historical "Average" temperatures (mean, min, and max)
  average_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
                      mean_max_min = as.character(rep(temp, times = 2)),
                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
                      value = as.numeric(c(actual_vals, average_vals))))
}

link_dates <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), to = Sys.Date(), by = "days"))
airport <- "KDSM/"

## WORKING ###
df3 <- data.frame(Dates = link_dates[1:365])
system.time(df3 %>% nest() %>% mutate(daily_temps = Dates %>% purrr::map(grab_temps2))) #%>% select(-Links) %>% unnest()
##############

```

### 2017-04-08 Web_Scraping_attempt3.Rmd
Add files via upload

--- 2017-04-08 Web_Scraping_attempt2.Rmd
@@
 
-*html_session within function *
-
-4/8/17  1:44pm    SYSTEM.TIME:  336.107 seconds elapsed
+*html_session within function with record inside the function (and not a separate function)*
 
@@
   s <- html_session("https://www.wunderground.com/history/airport/")
-  ss <- s %>% jump_to(paste0("KDSM/",link))
+  ss <- s %>% jump_to(paste0("KDSM/", link))
   html <- read_html(ss)
@@
 
-    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
-                      mean_max_min = as.character(rep(temp, times = 2)),
-                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
-                      value = as.numeric(c(actual_vals, average_vals))))
+    record <- html %>% 
+      html_nodes("#historyTable tr:nth-child(4) td:nth-child(4) , #historyTable tr:nth-child(3) td:nth-child(4)") %>%
+      html_text()
+    record_vals <- c("NA", parse_number(record))
+    record_yrs <- record %>% gsub("^[^\\(]+", "", .) %>% parse_number()
+
+    return(data.frame(day = as.Date(c(rep(substring(text = link, first = 1, last = 10), times = 6), "NA",
+                              paste0(record_yrs, substring(text = link, first = 5, last = 10)))),
+                      mean_max_min = as.character(rep(temp, times = 3)),
+                      actual_ave_rec = as.character(rep(c("Actual", "Historical Average", "Record"), each = 3)),
+                      value = as.numeric(c(actual_vals, average_vals, record_vals))))
 }
 
-## WORKING ###
-df2 <- data.frame(Links = links[1:365])
-system.time(df2 %>% nest() %>% mutate(daily_temps = Links %>% purrr::map(grab_temps))) #%>% select(-Links) %>% unnest()
-##############
+df2 <- data.frame(Links = links[1:3])  ## for first 3 'days'
+df2 %>% nest() %>% mutate(daily_temps = Links %>% purrr::map(grab_temps)) %>% select(-Links) #%>% unnest()
 
 ```
-
-*Pasting togeter url and then using read_html*
-
-4/8/17  1:52pm   SYSTEM.TIME:   343.802 elapsed
-
-```{r}
-
-grab_temps2 <- function(date){
-    url <- paste0("https://www.wunderground.com/history/airport/", "KDSM/", date, "/DailyHistory.html") # Pasting together parts of url
-    html <- read_html(url)
-
-  actual_vals <- html %>% 
-      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))
-
-    # grabbing the historical "Average" temperatures (mean, min, and max)
-  average_vals <- html %>% 
-      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))
-
-    # grabbing the labels for the temperature values
-    temp <- html %>% 
-      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
-      html_text()
-
-    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
-                      mean_max_min = as.character(rep(temp, times = 2)),
-                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
-                      value = as.numeric(c(actual_vals, average_vals))))
-}
-
-link_dates <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), to = Sys.Date(), by = "days"))
-airport <- "KDSM/"
-
-## WORKING ###
-df3 <- data.frame(Dates = link_dates[1:365])
-system.time(df3 %>% nest() %>% mutate(daily_temps = Dates %>% purrr::map(grab_temps2))) #%>% select(-Links) %>% unnest()
-##############
-
-```

### 2017-04-09 Web_Scraping_Final.Rmd
Add files via upload

---
title: 'Web Scraping: attempt 2'
author: "Katie Will"
date: "April 8, 2017"
output: html_document
---

*daily temperatures (approximately 26,000 days for DSM)*

```{r}

dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), 
                                                                 to = as.Date("2017-03-31"), by = "days"))
links_all <- paste0(dates_all, "/DailyHistory.html")

grab_act_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0(airport, "/", link))
  html <- read_html(ss)

   actual_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(2) , #historyTable tr:nth-child(3) td:nth-child(2), #historyTable tr:nth-child(2) td:nth-child(2)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
                      mean_max_min = as.character(temp),
                      actual_ave_rec = as.character(rep("Actual", times = 3)),
                      value = as.numeric(actual_vals)))
}

airport <- "KDSM"
DSM_daily <- data.frame(Links = links_all)  
DSM_daily <- DSM_daily %>% nest() %>% mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
                  select(-Links) %>% unnest(data) %>% unnest(daily_temps) %>% as.data.frame()

```

*average and record temperatures (366 days)*
```{r}

dates_2016 <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("2016-01-01"), 
                                                                  to = as.Date("2016-12-31"), by = "days"))
links_2016 <- paste0(dates_2016, "/DailyHistory.html")

grab_ave_rec_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KDSM/", link))
  html <- read_html(ss)

    # grabbing the historical "Average" temperatures (mean, min, and max)
    average_vals <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(3) , #historyTable tr:nth-child(3) :nth-child(3), #historyTable tr:nth-child(2) td:nth-child(3)") %>% html_text() %>% gsub("\n", "", .) %>% parse_number(., na = c("-", "NA"))

    # grabbing the labels for the temperature values
    temp <- html %>% 
      html_nodes("tr:nth-child(4) .indent , tr:nth-child(3) .indent, tr:nth-child(2) .indent") %>% 
      html_text()

    record <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(4) , #historyTable tr:nth-child(3) td:nth-child(4)") %>%
      html_text()
    record_vals <- c("NA", parse_number(record))
    record_yrs <- record %>% gsub("^[^\\(]+", "", .) %>% parse_number()

    return(data.frame(day = as.Date(c(rep(substring(text = link, first = 1, last = 10), times = 3), "NA",
                              paste0(record_yrs, substring(text = link, first = 5, last = 10)))),
                      mean_max_min = as.character(rep(temp, times = 2)),
                      ave_rec = as.character(rep(c("Historical Average", "Record"), each = 3)),
                      value = as.numeric(c(average_vals, record_vals))))
}

airport <- "KDSM"
DSM_ave_rec <- data.frame(Links = links_2016)  
DSM_ave_rec <- DSM_ave_rec %>% nest() %>% 
  mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
  select(-Links) %>% unnest(data) %>% unnest(ave_rec_temps) %>% as.data.frame()

```

### 2017-04-09 Web_Scraping_Final.Rmd
update scraping, save dsm data

@@
 ---
+### Notes for use:  
+\begin{enumerate}
+\item Change "airport" (line 46, line 90)
+\item Change name of data frame when calling function to e.g. (DSM, IAH, FAR)
+\item Make sure those name changes are in each place it gets called
+\item Change `city = "Des Moines, IA"` to correct city, state in mutate function
+\item Update save function to have the correct file and .csv name
+\end{enumerate}
 
@@
 ```{r}
-
+library(beepr)
+library(tidyverse)
+library(rvest)
 dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), 
@@
 
-    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
+    return(data.frame(date = as.Date(substring(text = link, first = 1, last = 10)),
                       mean_max_min = as.character(temp),
@@
 DSM_daily <- data.frame(Links = links_all)  
-DSM_daily <- DSM_daily %>% nest() %>% mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
+DSM_daily <- DSM_daily %>% nest() %>% 
+  mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
                   select(-Links) %>% unnest(data) %>% unnest(daily_temps) %>% as.data.frame()
-
+beepr::beep(8)
 ```
@@
 
-    return(data.frame(day = as.Date(c(rep(substring(text = link, first = 1, last = 10), times = 3), "NA",
+    return(data.frame(date = as.Date(c(rep(substring(text = link, first = 1, last = 10), times = 3), "NA",
                               paste0(record_yrs, substring(text = link, first = 5, last = 10)))),
                       mean_max_min = as.character(rep(temp, times = 2)),
-                      ave_rec = as.character(rep(c("Historical Average", "Record"), each = 3)),
+                      actual_ave_rec = as.character(rep(c("Historical Average", "Record"), each = 3)),
                       value = as.numeric(c(average_vals, record_vals))))
@@
 ```
+
+*put two datasets together and add some elements*
+```{r}
+head(DSM_daily)
+#names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
+head(DSM_ave_rec)
+#names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
+DSM_temps <- rbind(DSM_daily, DSM_ave_rec)
+
+DSM_temps <- DSM_temps %>% mutate(airport = airport)
+DSM_temps <- DSM_temps %>% mutate(city = "Des Moines, IA") # change this each time
+
+DSM_temps <- DSM_temps %>% mutate(day = lubridate::day(date),
+                                  month = lubridate::month(date),
+                                  year = lubridate::year(date))
+```
+
+*save final dataset*
+```{r}
+save(DSM_temps, file = "raw-data/DSM_temps.csv")
+```

### 2017-04-09 static visual.Rmd
create static visual file

---
title: "static visual"
author: "Kiegan Rice"
date: "April 9, 2017"
output: html_document
---

*install stuff*
```{r}
# installing ish
library(tidyverse)
library(beepr)
```

*read data*
```{r}
temps <- read.csv(file = "./raw-data/DSM_temps.csv")
head(temps)
```

*get dates in right format*
```{r}
dates_2016 <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("2016-01-01"), 
                                                                  to = as.Date("2016-12-31"), by = "days"))

temps <- temps %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
```

*base of plot*
```{r}
base <- temps %>% ggplot(aes(x = date_2016))
base
```

*record layer*
```{r}
data_record <- temps %>% filter(actual_ave_rec == "Record") %>% group_by(date_2016) %>%
  spread(key = mean_max_min, value = value)

layer_record <- geom_point(data = data_record, aes(x = date_2016+1, y = data_record$`Min Temperature`))
layer_record <- geom_rect(data = data_record, aes(xmin = date_2016-.5, xmax = date_2016+.5, ymin = data_record$`Min Temperature`, ymax = data_record$`Max Temperature`, fill = "black"))

base + layer_record
```

### 2017-04-10 static visual.Rmd
static fix

@@
 
-temps <- temps %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
+temps <- temps %>% select(-X) %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
 ```
@@
 ```{r}
-base <- temps %>% ggplot(aes(x = date_2016))
+base <- temps %>% ggplot(aes(x = date_2016)) + 
+  theme_classic() +
+  theme(panel.grid.major.x = element_line(colour = c("black", rep("grey", times = 11)), linetype = c(0, rep(2, times = 11))),
+        axis.text.x = element_text(hjust = -0.9), 
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.line.y = element_line(colour = "darkgrey")) +
+  scale_x_date(date_breaks = "1 month", 
+               date_labels = "%b", 
+               expand=c(0,0)) + 
+  scale_y_continuous(breaks = seq(-20, 120, by = 20), limits= c(-40, 120)) + 
+  xlab("") +
+  ylab("")
+
+text_layer_description <- annotate("text", 
+                                   label = "Bars represent the range between the daily high and low.",
+                                   x = lubridate::ymd("2016-07-24"),
+                                   y = -28, hjust = "center", size = 2.3)
+
+base <- base + text_layer_description
 base 
@@
 *record layer*
+```{r, fig.width = 10}
+data_record <- temps %>% select(-date, -year) %>% 
+  filter(actual_ave_rec == "Record", mean_max_min != "Mean Temperature") %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
+
+layer_record <- geom_rect(data = data_record, aes(xmin = date_2016, xmax = date_2016+1, ymin = data_record$`Min Temperature`, ymax = data_record$`Max Temperature`), fill = "#E6E5DD", alpha = 0.8)
+
+legend_layer_record <- geom_rect(aes(xmin = lubridate::ymd("2016-07-22"), 
+                                     xmax =  lubridate::ymd("2016-07-27"), 
+                                     ymin = -15, 
+                                     ymax = 15), 
+                                 fill = "#E6E5DD", alpha = 0.8)
+text_layer_record <-  annotate("text",
+                               label = c("Record Low", "Record High"), 
+                               x =  c(lubridate::ymd("2016-07-22"), lubridate::ymd("2016-07-22")), 
+                               y = c(-15, 15), 
+                               hjust = "right", 
+                               size = 2.3)
+
+records_plot <- base + 
+  layer_record + legend_layer_record + text_layer_record
+
+records_plot
+```
+
+*historical averages layer*
 ```{r}
-data_record <- temps %>% filter(actual_ave_rec == "Record") %>% group_by(date_2016) %>%
-  spread(key = mean_max_min, value = value)
+data_average <- temps %>% select(-date, -year) %>% 
+  filter(actual_ave_rec == "Historical Average", mean_max_min != "Mean Temperature") %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
 
-layer_record <- geom_point(data = data_record, aes(x = date_2016+1, y = data_record$`Min Temperature`))
-layer_record <- geom_rect(data = data_record, aes(xmin = date_2016-.5, xmax = date_2016+.5, ymin = data_record$`Min Temperature`, ymax = data_record$`Max Temperature`, fill = "black"))
+layer_average <- geom_rect(data = data_average, aes(xmin = date_2016, xmax = date_2016+1, 
+                                                   ymin = data_average$`Min Temperature`, ymax = data_average$`Max Temperature`), 
+                           fill = "#BCACAC", alpha = 0.8)
 
-base + layer_record
+legend_layer_average <- geom_rect(aes(xmin = lubridate::ymd("2016-07-24")-0.5, 
+                                     xmax =  lubridate::ymd("2016-07-25")+0.5, 
+                                     ymin = -10, 
+                                     ymax = 10), 
+                                 fill = "#BCACAC", alpha = 0.8)
+
+text_layer_average <-  annotate("text",
+                                label = "Normal range", 
+                                x =  lubridate::ymd("2016-07-19"), 
+                                y = 0, 
+                                hjust = "right", 
+                                size = 2.3)
+
+line_layer_average_ver <- geom_segment(aes(x = lubridate::ymd("2016-07-20"), 
+                                       xend = lubridate::ymd("2016-07-20"), 
+                                       y = -10, 
+                                       yend = 10), 
+                                   size = 0.01)
+
+line_layer_average_hor1 <- geom_segment(aes(x = lubridate::ymd("2016-07-20"),
+                   xend = lubridate::ymd("2016-07-22"),
+                   y = 10,
+                   yend = 10),
+               size = 0.01)
+
+line_layer_average_hor2 <- geom_segment(aes(x = lubridate::ymd("2016-07-20"),
+                   xend = lubridate::ymd("2016-07-22"),
+                   y = -10,
+                   yend = -10),
+               size = 0.01)
+
+averages_plot <- base + layer_average + 
+  legend_layer_average + text_layer_average + 
+  line_layer_average_ver + line_layer_average_hor1 + line_layer_average_hor2
+
+records_averages_plot <- records_plot + layer_average + 
+  legend_layer_average + text_layer_average + 
+  line_layer_average_ver + line_layer_average_hor1 + line_layer_average_hor2
+
+averages_plot
+records_averages_plot
 ```
+
+*actual temps layer*
+```{r, fig.width = 12, fig.height=4}
+data_actual <- temps %>% 
+  filter(actual_ave_rec == "Actual", year == 2015) %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
+
+layer_actual <- geom_rect(data = data_actual, aes(xmin = date_2016-.5, xmax = date_2016+.5, 
+                                                   ymin = data_actual$`Min Temperature`, ymax = data_actual$`Max Temperature`), 
+                           fill = "maroon")
+layer_white_ylines <- geom_hline(yintercept = seq(-20, 100, by = 20), colour = "white", lwd = 0.1)
+
+legend_layer_actual <- geom_rect(aes(xmin = lubridate::ymd("2016-07-24")-0.05, 
+                                     xmax =  lubridate::ymd("2016-07-25")+0.15, 
+                                     ymin = -5, 
+                                     ymax = 12), 
+                                 fill = "maroon")
+
+text_layer_actual <-  annotate("text",
+                               label = c("Actual Low", "Actual High"), 
+                               x =  c(lubridate::ymd("2016-07-29"), lubridate::ymd("2016-07-29")), 
+                               y = c(-5, 12), 
+                               hjust = "left", 
+                               size = 2.3)
+
+line_layer_actual_hor1 <- geom_segment(aes(x = lubridate::ymd("2016-07-24"),
+                   xend = lubridate::ymd("2016-07-28"),
+                   y = -5,
+                   yend = -5),
+               size = 0.01)
+
+line_layer_actual_hor2 <- geom_segment(aes(x = lubridate::ymd("2016-07-24"),
+                   xend = lubridate::ymd("2016-07-28"),
+                   y = 12,
+                   yend = 12),
+               size = 0.01)
+
+actual_plot <- base + layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+all_plot <- records_plot + 
+  layer_average + 
+  legend_layer_average + text_layer_average + 
+  line_layer_average_ver + line_layer_average_hor1 + line_layer_average_hor2 + 
+  layer_white_ylines +
+  layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+records_actual_plot <- records_plot + 
+    layer_white_ylines +
+  layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+averages_actual_plot <- averages_plot + 
+    layer_white_ylines +
+  layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+records_plot
+averages_plot
+actual_plot
+records_averages_plot
+records_actual_plot
+averages_actual_plot
+all_plot
+beep(8)
+```

### 2017-04-10 shiny/app.R
first go at shiny

@@ -1,38 +1,230 @@
 library(shiny)
-require(ggplot2)
+require(tidyverse)
 require(dplyr)
 
+temps <- read.csv("../raw-data/DSM_temps.csv")
 # Define UI for application that draws a histogram
-ui <- fluidPage(    
-  # Application title
-  titlePanel("Hello Shiny World!"),
+shinyApp(
+  ui = navbarPage(
+    "NYT Weather Chart",
+    tabPanel("Single Year",
+             inputPanel(sliderInput("yearSlider", label = "Year:",
+                                    min = 1945, max = 2016, step = 1, sep = "",value = 2015),
+                        
+                        checkboxGroupInput("checkLayer", label = ("Data Layers:"), 
+                                           choices = list("Record Values" = "RV", 
+                                                          "Historical Averages" = "HA", 
+                                                          "Daily for Current Year" = "DC"))),
+             plotOutput('tempsplot'),
+             verbatimTextOutput('selected'))),
   
-  # Sidebar with a slider input for the number of bins
-  sidebarPanel(
-    sliderInput("num",
-                "Number of Samples:",
-                min = 1,
-                max = 5000,
-                value = 2500)
-  ),
   
-  # Show a plot of the generated distribution
-  mainPanel(
-    plotOutput("hist")
-  )
-)
-
-# Define server logic required to draw a histogram
-server <- function(input, output) {
-  output$hist <- renderPlot({
-    dist <- rnorm(n = input$num)
-    gg <- data.frame(dist) %>% 
-      ggplot(aes(x = dist)) + geom_histogram(binwidth = 0.25) +
-      xlim(c(-10,10))
-    print(gg)
-  })
-}
-
-# Bind ui and server together
-shinyApp(ui, server)
-
+  server = function(input, output, session){
+    
+    
+    ####### REACTIVE FOR SINGLE YEAR TABLE #######
+    gg <- reactive({
+      
+      ############# BASE AND GENERAL SET-UP #############
+      dates_2016 <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("2016-01-01"), 
+                                                                   to = as.Date("2016-12-31"), by = "days"))
+      temps <- temps %>% select(-X) %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
+      base <- temps %>% ggplot(aes(x = date_2016)) + 
+        theme_classic() +
[…]

### 2017-04-11 shiny/app.R
FIX SHINY

@@ -12,9 +12,9 @@ shinyApp(
                                     min = 1945, max = 2016, step = 1, sep = "",value = 2015),
                         
                         checkboxGroupInput("checkLayer", label = ("Data Layers:"), 
-                                           choices = list("Record Values" = "RV", 
-                                                          "Historical Averages" = "HA", 
-                                                          "Daily for Current Year" = "DC"))),
+                                           choices = list("Record Values" = 1, 
+                                                          "Historical Averages" = 2, 
+                                                          "Daily for Current Year" = 3))),
              plotOutput('tempsplot'),
              verbatimTextOutput('selected'))),
   
@@ -195,23 +195,23 @@ shinyApp(
       else if(length(input$checkLayer) == 3){
         display_plot <- all_plot
       }
-      else if(input$checkLayer[1] == "RV" & input$checkLayer[2] == "HA"){
-        display_plot <- records_averages_plot
-      }
-      else if(input$checkLayer[1] == "RV" & input$checkLayer[2] == "DC"){
-        display_plot <- records_actual_plot
-      }
-      else if(input$checkLayer[1] == "HA" & input$checkLayer[2] == "DC"){
-        display_plot <- averages_actual_plot
-      }
-      else if(input$checkLayer == "DC"){
+      else if(length(input$checkLayer) == 1 & input$checkLayer[1] == "3"){
         display_plot <- actual_plot
       }
-      else if(input$checkLayer == "HA"){
+      else if(length(input$checkLayer) == 1 & input$checkLayer[1] == "2"){
         display_plot <- averages_plot
       }
-      else if(input$checkLayer == "RV"){
+      else if(length(input$checkLayer) == 1 & input$checkLayer[1] == "1"){
         display_plot <- records_plot
+      }
+      else if(input$checkLayer[1] == "1" & input$checkLayer[2] == "2"){
+        display_plot <- records_averages_plot
+      }
+      else if(input$checkLayer[1] == "1" & input$checkLayer[2] == "3"){
+        display_plot <- records_actual_plot
+      }
+      else if(input$checkLayer[1] == "2" & input$checkLayer[2] == "3"){
+        display_plot <- averages_actual_plot
       }
       else{
         display_plot <- base
@@ -224,7 +224,7 @@ shinyApp(
       gg()
     })
     output$selected = renderText({
-      input$checkLayer
+      input$checkLayer[1] == "1"
     })
     })
     

### 2017-04-11 Web_Scraping_Final.Rmd
oopsie fix

@@
 
-airport <- "KDSM"
-DSM_daily <- data.frame(Links = links_all)  
-DSM_daily <- DSM_daily %>% nest() %>% 
+airport <- "KORD"
+ORD_daily <- data.frame(Links = links_all)  
+ORD_daily <- ORD_daily %>% nest() %>% 
   mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
@@
   s <- html_session("https://www.wunderground.com/history/airport/")
-  ss <- s %>% jump_to(paste0("KDSM/", link))
+  ss <- s %>% jump_to(paste0("KORD/", link))
   html <- read_html(ss)
@@
 
-airport <- "KDSM"
-DSM_ave_rec <- data.frame(Links = links_2016)  
-DSM_ave_rec <- DSM_ave_rec %>% nest() %>% 
+airport <- "KORD"
+ORD_ave_rec <- data.frame(Links = links_2016)  
+ORD_ave_rec <- ORD_ave_rec %>% nest() %>% 
   mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
@@
 ```{r}
-head(DSM_daily)
+head(ORD_daily)
 #names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-head(DSM_ave_rec)
+head(ORD_ave_rec)
 #names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-DSM_temps <- rbind(DSM_daily, DSM_ave_rec)
+ORD_temps <- rbind(ORD_daily, ORD_ave_rec)
 
-DSM_temps <- DSM_temps %>% mutate(airport = airport)
-DSM_temps <- DSM_temps %>% mutate(city = "Des Moines, IA") # change this each time
+ORD_temps <- ORD_temps %>% mutate(airport = airport)
+ORD_temps <- ORD_temps %>% mutate(city = "Chicago, IL") # change this each time
 
-DSM_temps <- DSM_temps %>% mutate(day = lubridate::day(date),
+ORD_temps <- ORD_temps %>% mutate(day = lubridate::day(date),
                                   month = lubridate::month(date),
@@
 ```{r}
-save(DSM_temps, file = "raw-data/DSM_temps.csv")
+write.csv(ORD_temps, file = "raw-data/ORD_temps.csv")
 ```

### 2017-04-11 static visual.Rmd

@@
 beep(8)
+
+if(input$checkLayer == 1){
+    gg <- records_plot
+      }
+      else if(input$checkLayer == 2){
+        averages_plot
+      }
+      else if(input$checkLayer == 3){
+        actual_plot
+      }
 ```

### 2017-04-11 Web_Scraping_Final.Rmd
Fix small thing in short function. Now in terms of "MSP" instead of "DSM"

--- 2017-04-09 Web_Scraping_Final.Rmd
@@
 library(rvest)
-dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), 
+dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1948-01-01"), 
                                                                  to = as.Date("2017-03-31"), by = "days"))
@@
 
-airport <- "KDSM"
-DSM_daily <- data.frame(Links = links_all)  
-DSM_daily <- DSM_daily %>% nest() %>% 
+airport <- "KMSN"
+MSN_daily <- data.frame(Links = links_all)  
+MSN_daily <- MSN_daily %>% nest() %>% 
   mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
@@
   s <- html_session("https://www.wunderground.com/history/airport/")
-  ss <- s %>% jump_to(paste0("KDSM/", link))
+  ss <- s %>% jump_to(paste0(airport, "/", link))
   html <- read_html(ss)
@@
 
-airport <- "KDSM"
-DSM_ave_rec <- data.frame(Links = links_2016)  
-DSM_ave_rec <- DSM_ave_rec %>% nest() %>% 
+airport <- "KMSN"
+MSN_ave_rec <- data.frame(Links = links_2016)  
+MSN_ave_rec <- MSN_ave_rec %>% nest() %>% 
   mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
@@
 ```{r}
-head(DSM_daily)
+head(MSN_daily)
 #names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-head(DSM_ave_rec)
+head(MSN_ave_rec)
 #names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-DSM_temps <- rbind(DSM_daily, DSM_ave_rec)
+MSN_temps <- rbind(MSN_daily, MSN_ave_rec)
 
-DSM_temps <- DSM_temps %>% mutate(airport = airport)
-DSM_temps <- DSM_temps %>% mutate(city = "Des Moines, IA") # change this each time
+MSN_temps <- MSN_temps %>% mutate(airport = airport)
+MSN_temps <- MSN_temps %>% mutate(city = "Madison, WI") # change this each time
 
-DSM_temps <- DSM_temps %>% mutate(day = lubridate::day(date),
+MSN_temps <- MSN_temps %>% mutate(day = lubridate::day(date),
                                   month = lubridate::month(date),
@@
 ```{r}
-save(DSM_temps, file = "raw-data/DSM_temps.csv")
+write.csv(MSN_temps, file = "raw-data/MSN_temps.csv")
 ```

### 2017-04-11 shiny/app.R
updating app with city

@@ -1,22 +1,27 @@
 library(shiny)
 require(tidyverse)
 require(dplyr)
+library(plotly)
 
-temps <- read.csv("../raw-data/DSM_temps.csv")
+#load("~/Desktop/IowaState/Semester4/Stat585X/Project/sun-shiny-weather/data/temps.Rda")
+##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
 # Define UI for application that draws a histogram
 shinyApp(
   ui = navbarPage(
-    "NYT Weather Chart",
+    "NYT Weather Chart: \n Major Midwestern Cities",
     tabPanel("Single Year",
-             inputPanel(sliderInput("yearSlider", label = "Year:",
+             inputPanel(selectInput("citySelect", label = "City:",
+                                    choices = unique(temps$city), selected = "Des Moines, IA"),
+                        sliderInput("yearSlider", label = "Year:",
                                     min = 1945, max = 2016, step = 1, sep = "",value = 2015),
                         
                         checkboxGroupInput("checkLayer", label = ("Data Layers:"), 
                                            choices = list("Record Values" = 1, 
                                                           "Historical Averages" = 2, 
                                                           "Daily for Current Year" = 3))),
-             plotOutput('tempsplot'),
-             verbatimTextOutput('selected'))),
+             plotOutput('tempsplot')#,
+             #verbatimTextOutput('selected')
+             )),
   
   
   server = function(input, output, session){
@@ -28,7 +33,7 @@ shinyApp(
       ############# BASE AND GENERAL SET-UP #############
       dates_2016 <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("2016-01-01"), 
                                                                    to = as.Date("2016-12-31"), by = "days"))
-      temps <- temps %>% select(-X) %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
+      temps <- temps %>% select(-X) %>% filter(city == input$citySelect) %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
       base <- temps %>% ggplot(aes(x = date_2016)) + 
         theme_classic() +
         theme(panel.grid.major.x = element_line(colour = c("black", rep("grey", times = 11)), linetype = c(0, rep(2, times = 11))),
@@ -128,7 +133,7 @@ shinyApp(
[…]

### 2017-04-11 Web_Scraping_Final.Rmd

--- 2017-04-11 Web_Scraping_Final.Rmd
@@
   s <- html_session("https://www.wunderground.com/history/airport/")
-  ss <- s %>% jump_to(paste0("KORD/", link))
+  ss <- s %>% jump_to(paste0(airport, "/", link))
   html <- read_html(ss)

### 2017-04-13 raw-to-full.Rmd
combining all datasets

---
title: "raw-to-full"
author: "Kiegan Rice"
date: "April 11, 2017"
output: html_document
---

```{r}
DSM_temps <- read.csv("raw-data/DSM_temps.csv")
FAR_temps <- read.csv("raw-data/FAR_temps.csv")
MSN_temps <- read.csv("raw-data/MSN_temps.csv")
MSP_temps <- read.csv("raw-data/MSP_temps.csv")
ORD_temps <- read.csv("raw-data/ORD_temps.csv")

temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps)

save(temps, file = "data/temps.Rda")
```

### 2017-04-16 raw-to-full.Rmd
stuff

@@
 ORD_temps <- read.csv("raw-data/ORD_temps.csv")
+FSD_temps <- read.csv("raw-data/FSD_temps.csv")
+STL_temps <- read.csv("raw-data/STL_temps.csv")
 
-temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps)
+temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps, FSD_temps, STL_temps)
 

### 2017-04-16 Paper.Rmd
paper file

---
title: "A (sun)Shiny Recreation of the New York Times \n Weather Chart"
author: "Amy Crawford, Kiegan Rice, and Katie Will"
header-includes:
   - \usepackage{float}
geometry: margin=2cm
fontsize: 11pt
output: 
  pdf_document:
    number_sections: true
    fig_caption: yes
abstract: "In 1979 The New York Times published what would become a classic visualization of weather data that maps how temperatures compare to historic averages and records over the course of one year. This visualization has changed in several ways over the years, and in 2016 The New York Times published an online, interactive version of this chart, displaying 2015 temperature data for 3,116 world cities. In this project, we scrape historical data from [Weather Underground](https://www.wunderground.com/) for multiple cities for the years 1945 to 2017. With this data, we recreate the interactive chart published by The New York Times and allow for user interaction via a shiny app. Although we do not include all 3,116 cities, our app includes extra features that allow for users to view the data over the course of many years and choose the features they would like to include on their version of this iconic chart."
---

\section{Introduction}

\section{Methods}

\subsection{Scraping the Data}

\subsection{Creating a Static Visual}

\subsection{Introducing Shiny Interactivity}

\section{Results (maybe call this Outcomes?)}

\section{Discussion}

\section{Future Work}

### 2017-04-16 shiny/app.R
Adding Spag Plot

@@ -21,7 +21,13 @@ shinyApp(
                                                           "Daily for Current Year" = 3))),
              plotOutput('tempsplot')#,
              #verbatimTextOutput('selected')
-             )),
+             ),
+    
+    tabPanel("Spaghetti Plot",
+             inputPanel(selectInput("citySelectSpag", label = "City:",
+                                    choices = unique(temps$city), selected = "Des Moines, IA"),
+             plotOutput('spagplot')))
+    ),
   
   
   server = function(input, output, session){
@@ -228,8 +234,74 @@ shinyApp(
     output$tempsplot = renderPlot({
       gg()
     })
-    #output$selected = renderText({
-    #  input$checkLayer[1] == "1"
-    #})
+
+    
+#################### SPAG PLOT THINGS BELOW HERE ##############################  
+    
+    ####### REACTIVE FOR SINGLE YEAR TABLE #######
+    gg_spag <- reactive({ 
+      temps_spag <- temps %>% 
+        select(-X) %>% filter(city == input$citySelectSpag, 
+                              actual_ave_rec == "Actual", 
+                              mean_max_min == "Mean Temperature") %>% 
+        mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
+      
+      base_spag <- temps_spag %>% filter(year < 2016) %>%
+        ggplot(aes(x = date_2016, y = value, group = year)) + 
+        geom_line(colour = "grey") + 
+        theme_classic() +
+        theme(panel.grid.major.x = element_line(colour = c("black", rep("grey", times = 11)), linetype = c(0, rep(2, times = 11))),
+              axis.text.x = element_text(hjust = -0.9), 
+              axis.line.x = element_blank(),
+              axis.ticks.x = element_blank(),
+              axis.line.y = element_line(colour = "darkgrey")) +
+        scale_x_date(date_breaks = "1 month", 
+                     date_labels = "%b", 
+                     expand=c(0,0)) + 
+        scale_y_continuous(breaks = seq(-20, 120, by = 20), limits= c(-40, 120)) + 
+        xlab("") +
+        ylab("")
+      
+      layer_2016 <- geom_line(data = temps_spag[temps_spag$year == 2016,], aes(x = date_2016, y = value), colour = "maroon")
+   
[…]

### 2017-04-16 raw-to-full.Rmd
up

--- 2017-04-13 raw-to-full.Rmd
@@
 ORD_temps <- read.csv("raw-data/ORD_temps.csv")
+FSD_temps <- read.csv("raw-data/FSD_temps.csv")
+STL_temps <- read.csv("raw-data/STL_temps.csv")
+CMH_temps <- read.csv("raw-data/CMH_temps.csv")
+OMA_temps <- read.csv("raw-data/OMA_temps.csv")
+DET_temps <- read.csv("raw-data/DET_temps.csv")
 
-temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps)
+temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps, FSD_temps, STL_temps, CMH_temps, OMA_temps, DET_temps)
 

### 2017-04-16 shiny/app.R
Spag Plot functioning

@@ -25,8 +25,8 @@ shinyApp(
     
     tabPanel("Spaghetti Plot",
              inputPanel(selectInput("citySelectSpag", label = "City:",
-                                    choices = unique(temps$city), selected = "Des Moines, IA"),
-             plotOutput('spagplot')))
+                                    choices = unique(temps$city), selected = "Des Moines, IA")),
+             plotOutput('spagplot'))
     ),
   
   

### 2017-04-17 Paper.Rmd
adding notes section, future work bullets

@@
 
+```{r, echo = FALSE}
+# Notes:
+# - Some years there are missing values, they are replacing missing values with 0degreesF; 
+#       we will address this in the future work section unless we have time to deal with it before we present
+# - Why don't we just start at 1950 since all cities are started by then. Easier then changing where we start for each different city
+#
+#
+#
+#
+#
+```
+
 \section{Introduction}
@@
 \section{Future Work}  
+  - Fix data inconsistencies 
+  - Add in magic turning world
+  - Optimizing code
+  - Adding in ability to switch to celsius (?)
+  - Adding more cities 
+  - Add some sort of plotly interactivity/denote record years

### 2017-04-17 Paper.Rmd
Static Vis

@@
 
+The next magical step on our rainbow road to finishing 585X was to recreate the static New York Times weather chart. The original published chart
+
+We began by focusing on the city of Des Moines and created our first static visual using the data scraped for this city.
+
+In expectation of needing flexiblilty of choosing layers in a shiny app, we created the static visual in layers that can be easily peiced together to produce a variety of charts for which the user can choose the detail of the layers to be plotted.
+The base of the plot included the axes, theme, and legend that would remain consistent regardless of which layers were placed on top.
+The theme and major gridlines were chosen to match the orignal chart as closely as possible (with not too much effort though).
+Each of the dates were plotted for the year 2016 for the base as it includes a leap year and all of our historic averages and records were scraped from the most recent completed year (2016).
+Thus, regardless of which year the user may choose to plot, leap day averages and records will appear even if a daily temperature is not available.
+The chart represents three levels of historic weather information and we chose to create each of those layers along with their respective legends in separate stages.
+
+The first stage of the chart was created by graphing bars that spanned from the record low temperature to the record high temperature for each day over the course of one year.
+We then added a matching legend to the layer that would show up whenever the layer was present on the plot.
+The next layer was also constructed using bars, these spanned from the average low to the average high temperature for each calendar day, averaged accross all years.
+This layer also included its own portion of the legend that would plot whenever this layer was present.
+The final layer that was created included boxes that spanned from the daily high and low temperatures for each calendar day in 2015.
+This was the top layer and added the final piece of the legend to the plot.
+Along with this layer we also added faint white y-axis gridlines underneath as a reference point for viewers.
+
+FIGURE 1
+
 \subsection{Introducing Shiny Interactivity}

### 2017-04-17 Paper.Rmd
shiny words

@@
 \subsection{Introducing Shiny Interactivity}  
+\subsubsection{Classic Chart Recreation for a Single Year}
+
+Although we have a much smaller set of cities in our Shiny app, we wanted to include much of the same interactivity that the New York Times implemented, while also extending to add a few new ways that users could interact with the data.
+The main update we wanted to include was the ability to change which year the user wanted to have daily temperatures for.
+Although the original graphic allows for a lot of cool interpretability, the ability to compare across years is a huge advantage when investigating how weather trends have changed.
+Although we have daily temperature data ranging all the way back to 1945, the set of cities we are working with are inconsistent with their start dates.
+However, all cities in our data have daily temperatures beyond 1950, so we chose to make this element of the interactivity available for 1950 to 2016 only.
+Since the chart spans a full year, we do not include 2017 in the 'Single Year' tab of our Shiny app.
+Users can interact with data for the current year in the other tab, explained in section **something**.
+
+As already discussed in the scraping section, we have a limited scope of cities.
+However, the interactivity with city is essentially the same as the New York Times chart, with the exception of the super cool moving globe thing.
+Users can choose a midwestern city from a drop-down menu that includes all available cities (that the app creators have scraped up to this point).
+
+Users of the app can select which year they want to look at by moving a slider input across a variety of years.
+When users select a year, they are selecting which year they would like to see for the top layer.
+It is important to note that the record and historical averages layers will not change for any given city, no matter which year is selected.
+These are record values that are current through March 2017, either averaged with data from the current year (for average data), or updated when record data happens.
+
+The most innovative update to the interactive version of this chart (or at least we think so) is that the user may choose which layers of the plot they would like to view together.
+A user can look at any of the three layers individually, or any combination of the three layers.
+This allows users to see the chart in all its glory, or just examine a single aspect of the data for that given city and year.
+The base layer and gridlines remain constant, and as users check boxes to select which layers they want to examine, the layers are added or removed from this base plot accordingly.
+No matter which order the boxes are checked in, layers will always be added in the order they are meant to be in the original chart (i.e., records on the bottom, then averages, and finally the daily temperatures on top).
+This interactivity was made possible by a reactive function that creates 7 plots of the possible layer combinations for the city-year pair, and returns the one that matches the boxes that the user has checked.
+
+\subsubsection{Historic Spaghetti Monster Plot for a Single City}
 

### 2017-04-17 shiny/app.R
change ylim

@@ -50,7 +50,7 @@ shinyApp(
         scale_x_date(date_breaks = "1 month", 
                      date_labels = "%b", 
                      expand=c(0,0)) + 
-        scale_y_continuous(breaks = seq(-20, 120, by = 20), limits= c(-40, 120)) + 
+        scale_y_continuous(breaks = seq(-50, 120, by = 20), limits= c(-50, 120)) + 
         xlab("") +
         ylab("")
       
@@ -142,7 +142,7 @@ shinyApp(
       layer_actual <- geom_rect(data = data_actual, aes(xmin = date_2016, xmax = date_2016+1, 
                                                         ymin = data_actual$`Min Temperature`, ymax = data_actual$`Max Temperature`), 
                                 fill = "maroon")
-      layer_white_ylines <- geom_hline(yintercept = seq(-20, 100, by = 20), colour = "white", lwd = 0.1)
+      layer_white_ylines <- geom_hline(yintercept = seq(-40, 100, by = 20), colour = "white", lwd = 0.1)
       
       
       
@@ -258,7 +258,7 @@ shinyApp(
         scale_x_date(date_breaks = "1 month", 
                      date_labels = "%b", 
                      expand=c(0,0)) + 
-        scale_y_continuous(breaks = seq(-20, 120, by = 20), limits= c(-40, 120)) + 
+        scale_y_continuous(breaks = seq(-50, 120, by = 20), limits= c(-50, 120)) + 
         xlab("") +
         ylab("")
       

### 2017-04-17 Paper.Rmd
adding static figure to paper

@@
 \section{Methods}  
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+# installing ish
+library(tidyverse)
+library(gridExtra)
+temps <- read.csv(file = "./raw-data/DSM_temps.csv")
+#head(temps)
+dates_2016 <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("2016-01-01"), 
+                                                                  to = as.Date("2016-12-31"), by = "days"))
+temps <- temps %>% select(-X) %>% mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
+```
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+
+### BASE ###
+base <- temps %>% ggplot(aes(x = date_2016)) + 
+  theme_classic() +
+  theme(panel.grid.major.x = element_line(colour = c("black", rep("grey", times = 11)), linetype = c(0, rep(2, times = 11))),
+        axis.text.x = element_text(hjust = -0.9), 
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.line.y = element_line(colour = "darkgrey")) +
+  scale_x_date(date_breaks = "1 month", 
+               date_labels = "%b", 
+               expand=c(0,0)) + 
+  scale_y_continuous(breaks = seq(-20, 120, by = 20), limits= c(-40, 120)) + 
+  xlab("") +
+  ylab("")
+
+text_layer_description <- annotate("text", 
+                                   label = "Bars represent the range between the daily high and low.",
+                                   x = lubridate::ymd("2016-07-24"),
+                                   y = -28, hjust = "center", size = 2.3)
+
+base <- base + text_layer_description
+
+### RECORD ###
+data_record <- temps %>% select(-date, -year) %>% 
+  filter(actual_ave_rec == "Record", mean_max_min != "Mean Temperature") %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
+
+layer_record <- geom_rect(data = data_record, aes(xmin = date_2016, xmax = date_2016+1, ymin = data_record$`Min Temperature`, ymax = data_record$`Max Temperature`), fill = "#E6E5DD", alpha = 0.8)
+
+legend_layer_record <- geom_rect(aes(xmin = lubridate::ymd("2016-07-22"), 
+                                     xmax =  lubridate::ymd("2016-07-27"), 
+                                     ymin = -15, 
+                                     ymax = 15), 
+                                 fill = "#E6E5DD", alpha = 0.8)
+text_layer_record <-  annotate("text",
+                               label = c("Record Low", "Record High"), 
+                               x =  c(lubridate::ymd("2016-07-22"), lubridate::ymd("2016-07-22")), 
+                               y = c(-15, 15), 
+                               hjust = "right", 
+                               size = 2.3)
+
+records_plot <- base + 
+  layer_record + legend_layer_record + text_layer_record
+
+### AVERAGES ###
+data_average <- temps %>% select(-date, -year) %>% 
+  filter(actual_ave_rec == "Historical Average", mean_max_min != "Mean Temperature") %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
+
+layer_average <- geom_rect(data = data_average, aes(xmin = date_2016, xmax = date_2016+1, 
+                                                   ymin = data_average$`Min Temperature`, ymax = data_average$`Max Temperature`), 
+                           fill = "#BCACAC", alpha = 0.8)
+
+legend_layer_average <- geom_rect(aes(xmin = lubridate::ymd("2016-07-24")-0.5, 
+                                     xmax =  lubridate::ymd("2016-07-25")+0.5, 
+                                     ymin = -10, 
+                                     ymax = 10), 
+                                 fill = "#BCACAC", alpha = 0.8)
+
+text_layer_average <-  annotate("text",
+                                label = "Normal range", 
+                                x =  lubridate::ymd("2016-07-19"), 
+                                y = 0, 
+                                hjust = "right", 
+                                size = 2.3)
+
+line_layer_average_ver <- geom_segment(aes(x = lubridate::ymd("2016-07-20"), 
+                                       xend = lubridate::ymd("2016-07-20"), 
+                                       y = -10, 
+                                       yend = 10), 
+                                   size = 0.01)
+
+line_layer_average_hor1 <- geom_segment(aes(x = lubridate::ymd("2016-07-20"),
+                   xend = lubridate::ymd("2016-07-22"),
+                   y = 10,
+                   yend = 10),
+               size = 0.01)
+
+line_layer_average_hor2 <- geom_segment(aes(x = lubridate::ymd("2016-07-20"),
+                   xend = lubridate::ymd("2016-07-22"),
+                   y = -10,
+                   yend = -10),
+               size = 0.01)
+
+records_averages_plot <- records_plot + layer_average + 
+  legend_layer_average + text_layer_average + 
+  line_layer_average_ver + line_layer_average_hor1 + line_layer_average_hor2
+
+### ACTUAL ###
+data_actual <- temps %>% 
+  filter(actual_ave_rec == "Actual", year == 2015) %>% 
+  group_by(month, day) %>% spread(key = mean_max_min, value = value)
+
+layer_actual <- geom_rect(data = data_actual, aes(xmin = date_2016-.5, xmax = date_2016+.5, 
+                                                   ymin = data_actual$`Min Temperature`, ymax = data_actual$`Max Temperature`), 
+                           fill = "maroon")
+layer_white_ylines <- geom_hline(yintercept = seq(-20, 100, by = 20), colour = "white", lwd = 0.1)
+
+legend_layer_actual <- geom_rect(aes(xmin = lubridate::ymd("2016-07-24")-0.05, 
+                                     xmax =  lubridate::ymd("2016-07-25")+0.15, 
+                                     ymin = -5, 
+                                     ymax = 12), 
+                                 fill = "maroon")
+
+text_layer_actual <-  annotate("text",
+                               label = c("Actual Low", "Actual High"), 
+                               x =  c(lubridate::ymd("2016-07-29"), lubridate::ymd("2016-07-29")), 
+                               y = c(-5, 12), 
+                               hjust = "left", 
+                               size = 2.3)
+
+line_layer_actual_hor1 <- geom_segment(aes(x = lubridate::ymd("2016-07-24"),
+                   xend = lubridate::ymd("2016-07-28"),
+                   y = -5,
+                   yend = -5),
+               size = 0.01)
+
+line_layer_actual_hor2 <- geom_segment(aes(x = lubridate::ymd("2016-07-24"),
+                   xend = lubridate::ymd("2016-07-28"),
+                   y = 12,
+                   yend = 12),
+               size = 0.01)
+
+#actual_plot <- base + layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+all_plot <- records_plot + 
+  layer_average + 
+  legend_layer_average + text_layer_average + 
+  line_layer_average_ver + line_layer_average_hor1 + line_layer_average_hor2 + 
+  layer_white_ylines +
+  layer_actual + legend_layer_actual + text_layer_actual + line_layer_actual_hor1 + line_layer_actual_hor2
+
+```
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 5, fig.cap = "The static visual at each of the individual steps, as layers were created and added to the chart."}
+
+base1 <- base + labs(title = "Step 1: Creating a base")
+records_plot1 <- records_plot + labs(title = "Step 2: Adding the record values")
+records_averages_plot1 <- records_averages_plot + labs(title = "Step 3: Adding historical averages")
+all_plot1 <- all_plot + labs(title = "Step 4: Adding daily temperature values for 2015")
+grid.arrange(base1, records_plot1, records_averages_plot1, all_plot1, ncol = 2)
+```
 

### 2017-04-17 Paper.Rmd
future woRk

@@
 \section{Future Work}
-  - Fix data inconsistencies 
-  - Add in magic turning world
-  - Optimizing code
-  - Adding in ability to switch to celsius (?)
-  - Adding more cities 
-  - Add some sort of plotly interactivity/denote record years
+
+Although we believe this project has allowed us to successfully recreate an iconic weather chart and implement new interactive elements, there are still many improvements that could be made to this project.
+There are several elements of the New York Times interactive graphic that we did not include in ours; the cumulative precipitation chart for each month, the average temperature for the year and how it compares to historic averages, and the ability to switch the scale to Celsius instead of Fahrenheit.
+
+Although it would require a lot of extra time to scrape precipitation data, we believe this would be a useful addition to the chart if time allowed.
+The Weather Underground does not include snow in their precipitation totals, so we would have to also take that into consideration when adding that new element to the chart, especially since our current cities are all in regions that have snowfall each winter.
+
+In the top left corner of the original graphic, there is a note about what the year's average temperature was in that city, and how much higher or lower that overall average was than the historic average.
+As that was the focus of their chart on the interactive chart page, ``How Much Warmer Was Your City in 2015", it is difficult for statisticians to reconcile one overall average temperature for the entire year without any further explanation, especially for cities in which winter temperatures greatly vary from summer temperatures.
+We would like to explore other options to communicate this information, and perhaps find a more accurate or detailed way to display it to viewers.
+
+Although it would simply require a change in the axes and a transformation of the data, we did not create the option for users to change between Celsius and Fahrenheit.
+With all the other options available to users, it would be a bit clunky to also add in that transformation.
+
+The biggest roadblock for a lot of these issues is the code that we are working with.
+Scraping the data takes quite a while, because we have to open a link separately for each day we want data for in history.
+However, if we could find a quicker way to scrape this data, we would be very interested in expanding the scope of cities we have data for so that users have even more to work with.
+The framework we have set up for the Shiny interactivity also means that a lot of things have to happen to our data inside the app itself before we can display the image that the user would like to see; once we filter the data by city and year, the graphics themselves have to be created and then displayed based on which layers the user is interested in.
+If we could find a way to render much of this information outside of the 'reactive' statement or a better way to do it in general, we would be able to have more options and they would render more quickly.
+
+Finally, we would like to be able to add some interactivity with the `plotly` package, or at least be able to denote record temperatures that happen in a given year when they occur.
+The original chart denotes when record values happen and labels them with what the value of that record temperature was.
+If we could allow users to be able to scroll over the values for the current year, they could see what the actual values were that make up the different layers.
+However, as it stands at the moment, when `plotly` is added to the graphic, it is extremely slow and takes approximately 1 minute to render a single plot.
+This is clearly an unreasonable amount of time for a user to wait for an image, especially if they want to switch around layers quickly.
+
+Although we have not created an actual R package, we believe it would be a really fun interactive environment for users to look into, as well as for professors to use as teaching material - either about `ggplot2`, `shiny`, or just about interactive graphics in general.
+It may be advantageous to have this as a full R package available at least via GitHub, and let users know what they can do with the available data and the shiny app.

### 2017-04-17 Paper.Rmd
Static visual section update

@@
 
-The next magical step on our rainbow road to finishing 585X was to recreate the static New York Times weather chart. The original published chart
+After data collection we were able to begin building our static recreation of the New York Times weather chart.
+We made this first static visual using the historic records, averages, and daily temperatures for the city of Des Moines, IA.
+We created this chart for the year 2015 because at the time the New York Times had a 2015 weather chart for various cities available on their website and we were able to compare our results directly.
+In anticipation of the flexiblilty that would be required to allow future users to choose a combination of layers to be plotted in a Shiny app, we created the static visual as a base plot with many layers that could be easily placed together to produce many variations of the original chart.
 
-We began by focusing on the city of Des Moines and created our first static visual using the data scraped for this city.
+The base of the plot included the axes, theme, and legend that would remain constant regardless of which layers were placed on top.
+The theme and major gridlines were chosen to match the orignal chart as closely as possible and the y-axis limits were set to accomodate a large range of record temperatures for midwestern cities.
+Each of the dates on the x-axis of the base layer were plotted for the year 2016 because it includes a leap year and all historic averages and records were scraped from the most recent completed year (2016).
+Thus, regardless of which year the user may choose to plot, leap day averages and records will appear even if a daily temperature is not available.
 
-In expectation of needing flexiblilty of choosing layers in a shiny app, we created the static visual in layers that can be easily peiced together to produce a variety of charts for which the user can choose the detail of the layers to be plotted.
-The base of the plot included the axes, theme, and legend that would remain consistent regardless of which layers were placed on top.
-The theme and major gridlines were chosen to match the orignal chart as closely as possible (with not too much effort though).
-Each of the dates were plotted for the year 2016 for the base as it includes a leap year and all of our historic averages and records were scraped from the most recent completed year (2016).
-Thus, regardless of which year the user may choose to plot, leap day averages and records will appear even if a daily temperature is not available.
-The chart represents three levels of historic weather information and we chose to create each of those layers along with their respective legends in separate stages.
-
-The first stage of the chart was created by graphing bars that spanned from the record low temperature to the record high temperature for each day over the course of one year.
-We then added a matching legend to the layer that would show up whenever the layer was present on the plot.
-The next layer was also constructed using bars, these spanned from the average low to the average high temperature for each calendar day, averaged accross all years.
-This layer also included its own portion of the legend that would plot whenever this layer was present.
-The final layer that was created included boxes that spanned from the daily high and low temperatures for each calendar day in 2015.
-This was the top layer and added the final piece of the legend to the plot.
-Along with this layer we also added faint white y-axis gridlines underneath as a reference point for viewers.
-
-FIGURE 1
+The remainder of the chart was simply built by creating three layers containing seperate visuals of the historic records, averages, and daily temperatures and adding these visuals as layers to the base plot in a particular order.
+The first layer to be added to the base of the chart was for the historic records.
+This layer was created by graphing bars that spanned from the record low temperature to the record high temperature for each day over the course of one year.
+A matching legend was added to the layer and would show up whenever the layer was present on the plot.
+The next layer was constructed using bars, this time spanning from the average low to the average high temperature for each calendar day, averaged accross all years.
+This layer also included its own matching portion of legend that would plot whenever this layer was present.
+The final layer was created in a similar fashion to include boxes spanning from the daily high and low temperatures for each calendar day in 2015.
+This was the top layer and added the final data visual to the plot as well as the final piece of the legend.
+Along with this layer we also added faint white y-axis gridlines underneath it that would cross over the previous two layers and act as a reference point for viewers.
 

### 2017-04-17 shiny/app.R
add current temp dot

@@ -2,6 +2,7 @@ library(shiny)
 require(tidyverse)
 require(dplyr)
 library(plotly)
+library(rvest)
 
 #load("~/Desktop/IowaState/Semester4/Stat585X/Project/sun-shiny-weather/data/temps.Rda")
 ##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
@@ -18,7 +19,9 @@ shinyApp(
                         checkboxGroupInput("checkLayer", label = ("Data Layers:"), 
                                            choices = list("Record Values" = 1, 
                                                           "Historical Averages" = 2, 
-                                                          "Daily for Current Year" = 3))),
+                                                          "Daily for Chosen Year" = 3), selected = c(1,2,3)),
+                        checkboxInput("currentTemp", label = "Add Current Temperature",
+                                           value = FALSE)),
              plotOutput('tempsplot')#,
              #verbatimTextOutput('selected')
              ),
@@ -227,6 +230,39 @@ shinyApp(
       else{
         display_plot <- base
       }
+      
+      
+      
+      ### add in if statement to scrape current temperature
+      if(length(input$checkLayer) > 0 & input$currentTemp == TRUE){
+        state <- gsub(".*\ ", "", input$citySelect)  ## getting state from the first entry in temps$city
+        city <- gsub(",.*", "", input$citySelect)  ## getting city from the first entry in temps$city
+        city <- gsub("\\.", "", city)  ## getting rid of "." if it exists in a city i.e. St. Louis
+        city <- gsub(" ", "_", city)  ## replacing a space with "_" i.e. St_Louis
+        
+        url <- paste0("https://www.wunderground.com/US/", state, "/", city, ".html")
+        html <- read_html(url)
+        
+        cur_temp <- html %>% html_nodes("#curTemp .wx-value") %>% html_text() %>% parse_number()
+        cur_date <- lubridate::ymd(paste0("2016", "-", lubridate::month(today()), "-", lubridate::day(today())))
+        
+        cur_point_layer <- geom_point(aes(x = cur_date, y = cur_temp), color = "black")
+        
+        cur_point_legend <-  annotate("text",
+                                      label = paste0("Current Temperature in ", input$citySelect), 
+                                      x =  cur_date, 
+                                      y = cur_temp + 25, 
+                                      hjust = "left", 
+                                      size = 3)
+        cur_point_legend_line <- geom_segment(aes(x = cur_date,
+                                                 xend = cur_date,
[…]

### 2017-04-17 Paper.Rmd
interactivity and outcomes

@@
 
-Although we have a much smaller set of cities in our Shiny app, we wanted to include much of the same interactivity that the New York Times implemented, while also extending to add a few new ways that users could interact with the data.
-The main update we wanted to include was the ability to change which year the user wanted to have daily temperatures for.
-Although the original graphic allows for a lot of cool interpretability, the ability to compare across years is a huge advantage when investigating how weather trends have changed.
-Although we have daily temperature data ranging all the way back to 1945, the set of cities we are working with are inconsistent with their start dates.
-However, all cities in our data have daily temperatures beyond 1950, so we chose to make this element of the interactivity available for 1950 to 2016 only.
+The New York Times weather chart allows users to select a city from a drop down menu and view dail temperatures for the year 2015 along with recoreds and averages.
+We wanted to keep this useful peice of interactivity and so our users can too chose a city to view from a drop down menu.
+As already discussed in the scraping section, we have a limited scope of cities.
+When a user choses one of the midwestern cities from the menu, the data is filtered to include temperatures for that city only.
+
+Next, we wanted to implement an interactive option that wasn't available on the NYT weather chart.
+We thought that by allowing users to view daily temperatures for a large range of years, not just for 2015 would be a large improvement.
+Some of the cities that we scraped data for have daily temperature data ranging all the way back to 1945, but unfortunately the full set of cities we are working with do not agree on this start date.
+All of the cities do have daily temperatures beyond 1950, so we chose to make this element of the interactivity available to users only for the years 1950 to 2016 in the form of a slider bar.
 Since the chart spans a full year, we do not include 2017 in the 'Single Year' tab of our Shiny app.
-Users can interact with data for the current year in the other tab, explained in section **something**.
+Users can view data for the current year in the other tab, explained in Section 2.3.2.
 
-As already discussed in the scraping section, we have a limited scope of cities.
-However, the interactivity with city is essentially the same as the New York Times chart, with the exception of the super cool moving globe thing.
-Users can choose a midwestern city from a drop-down menu that includes all available cities (that the app creators have scraped up to this point).
+When users select a single year, they are dictating the set of daily temperatures that will be filtered from the data and plotted in the top layer of the graphic.
+It is important to note that the record and historical averages layers will not change for any given city, no matter which year is selected.
+These are record values that are current through March 2017, either averaged with data from the current year (for average data), or updated when a record temperature occurs.
 
-Users of the app can select which year they want to look at by moving a slider input across a variety of years.
-When users select a year, they are selecting which year they would like to see for the top layer.
-It is important to note that the record and historical averages layers will not change for any given city, no matter which year is selected.
-These are record values that are current through March 2017, either averaged with data from the current year (for average data), or updated when record data happens.
-
-The most innovative update to the interactive version of this chart (or at least we think so) is that the user may choose which layers of the plot they would like to view together.
-A user can look at any of the three layers individually, or any combination of the three layers.
-This allows users to see the chart in all its glory, or just examine a single aspect of the data for that given city and year.
-The base layer and gridlines remain constant, and as users check boxes to select which layers they want to examine, the layers are added or removed from this base plot accordingly.
+Additionally, we decided to allow the user to select which layers of the visual they would like to view together.
+The base layer and gridlines will remain constant, and as users check boxes to select which layers they want to examine, the layers are added or removed from this base plot accordingly.
 No matter which order the boxes are checked in, layers will always be added in the order they are meant to be in the original chart (i.e., records on the bottom, then averages, and finally the daily temperatures on top).
-This interactivity was made possible by a reactive function that creates 7 plots of the possible layer combinations for the city-year pair, and returns the one that matches the boxes that the user has checked.
+This interactivity was made possible by a reactive function that creates seven plots of each possible layer combination for the city-year pair, and returns the one that matches the boxes that the user has checked.
 
@@
 
+While the original chart recreation in the 'Single Year' tab is very informative and flexible, it only allows users to inspect a single year at a time.
+We thought it would be nice if the user could compare temperature data for a single city over many years in one place so we created a spaghetti plot feature that resides in the 'Spaghetti Plot' tab of the Shiny app.
+
+Again, users are able to choose a city to investigate from a drop down menu.
+For the chosen city, the spaghetti plot is constructed with temperatures on the y-axis and month-day on the x-axis.
+Data is added to the chart by plotting a line through the average daily temperatures over the course of one year for each year.
+Lines for the years 1950 through 2015 are grey while the lines for 2016 and 2017 are colored so that the user is able to quickly see recent weather patterns and how they relate to previous years for a single city.
+
 \section{Results (maybe call this Outcomes?)}
+
+In the 'Single Year' tab of the Shiny app, users can interact with our recreation of the original chart.
+Although we have a much smaller set of cities in our Shiny app, we wanted to include much of the same interactivity that the New York Times implemented, while also extending to add a few new ways that users could interact with the data.
+The largest and most straight forward update that we wanted to include was the ability for users to choose which year to display daily temperatures for.
+The original graphic has many other impressive details, but the ability to view temperatures for a range of years will be a great advantage when investigating how weather trends change over time.
+Users of the app can select which year they want to look at by moving a slider input across a variety of years and the app reacts accordinly to change the top layer to reflect current temperatures for the chosen year.
+
+What we might deem the most innovative update to the interactive version of this chart is the flexibility and variety of viewing options that are available to the user.
+We allow the user to look at any of the three layers individually, or any combination of the three layers.
+This allows them to see the full graphic that resembles the original New York Times chart, or just examine a single aspect of the data for a specified city and year.
+
+In the 'Spaghetti Plot' tab the user can view average trends for a single city over multiple years in one graphic.
+This is advantagous to a user who is interested in assessing and comparing average weather trends between many years.
+Additionally this plot includes data for the year 2017, which the single year plot does not.
+In order to show the user what average temperatures have been doing lately, we highlight the latest complete year (2016) and the current incomplete year.
 

### 2017-04-17 shiny/app.R
submit butt

@@ -21,7 +21,8 @@ shinyApp(
                                                           "Historical Averages" = 2, 
                                                           "Daily for Chosen Year" = 3), selected = c(1,2,3)),
                         checkboxInput("currentTemp", label = "Add Current Temperature",
-                                           value = FALSE)),
+                                           value = FALSE),
+                        submitButton("Update View", icon("refresh"))),
              plotOutput('tempsplot')#,
              #verbatimTextOutput('selected')
              ),

### 2017-04-17 shiny/app.R
na omit

@@ -4,9 +4,12 @@ require(dplyr)
 library(plotly)
 library(rvest)
 
-#load("~/Desktop/IowaState/Semester4/Stat585X/Project/sun-shiny-weather/data/temps.Rda")
+#load("../data/temps.Rda")
 ##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
 # Define UI for application that draws a histogram
+temps <- temps %>% na.omit()
+
+
 shinyApp(
   ui = navbarPage(
     "NYT Weather Chart: \n Major Midwestern Cities",

### 2017-04-17 shiny/app.R
dot

@@ -4,7 +4,7 @@ require(dplyr)
 library(plotly)
 library(rvest)
 
-#load("../data/temps.Rda")
+#load("./data/temps.Rda")
 ##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
 # Define UI for application that draws a histogram
 temps <- temps %>% na.omit()

### 2017-04-17 shiny/app.R
load

@@ -4,7 +4,7 @@ require(dplyr)
 library(plotly)
 library(rvest)
 
-#load("./data/temps.Rda")
+load("temps.Rda")
 ##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
 # Define UI for application that draws a histogram
 temps <- temps %>% na.omit()

### 2017-04-17 shiny/app.R
data(temps)

@@ -4,7 +4,7 @@ require(dplyr)
 library(plotly)
 library(rvest)
 
-load("temps.Rda")
+data(temps)
 ##### I'm not sure why this did this... it is in the data folder so we should just be able to look at it
 # Define UI for application that draws a histogram
 temps <- temps %>% na.omit()

### 2017-04-17 shiny/app.R
add update button 2nd plot

@@ -32,7 +32,8 @@ shinyApp(
     
     tabPanel("Spaghetti Plot",
              inputPanel(selectInput("citySelectSpag", label = "City:",
-                                    choices = unique(temps$city), selected = "Des Moines, IA")),
+                                    choices = unique(temps$city), selected = "Des Moines, IA"),
+                        submitButton("Update View", icon("refresh"))),
              plotOutput('spagplot'))
     ),
   

### 2017-04-17 shiny/app.R
lub

@@ -249,7 +249,7 @@ shinyApp(
         html <- read_html(url)
         
         cur_temp <- html %>% html_nodes("#curTemp .wx-value") %>% html_text() %>% parse_number()
-        cur_date <- lubridate::ymd(paste0("2016", "-", lubridate::month(today()), "-", lubridate::day(today())))
+        cur_date <- lubridate::ymd(paste0("2016", "-", lubridate::month(lubridate::today()), "-", lubridate::day(lubridate::today())))
         
         cur_point_layer <- geom_point(aes(x = cur_date, y = cur_temp), color = "black")
         

### 2017-04-18 Paper.Rmd
things

@@
 
-\subsubsection{Historic Spaghetti Monster Plot for a Single City}
+\subsubsection{Spaghetti Plot for Many Years}
 
@@
 
-\section{Results (maybe call this Outcomes?)}
+\section{Outcomes}
 
-In the 'Single Year' tab of the Shiny app, users can interact with our recreation of the original chart.
-Although we have a much smaller set of cities in our Shiny app, we wanted to include much of the same interactivity that the New York Times implemented, while also extending to add a few new ways that users could interact with the data.
+In the 'Single Year' tab of the Shiny app, users can interact with our recreation of the original chart (see Figure 2).
+Although we have a much smaller set of cities in our Shiny app we wanted to include much of the same interactivity that the New York Times implemented, and extend to add a few new ways that users could interact with the data.
+
 The largest and most straight forward update that we wanted to include was the ability for users to choose which year to display daily temperatures for.
-The original graphic has many other impressive details, but the ability to view temperatures for a range of years will be a great advantage when investigating how weather trends change over time.
+The original graphic has many other impressive details, but the ability to view temperatures for a range of years will be a great advantage when investigating how weather trends change.
 Users of the app can select which year they want to look at by moving a slider input across a variety of years and the app reacts accordinly to change the top layer to reflect current temperatures for the chosen year.
 
-What we might deem the most innovative update to the interactive version of this chart is the flexibility and variety of viewing options that are available to the user.
-We allow the user to look at any of the three layers individually, or any combination of the three layers.
-This allows them to see the full graphic that resembles the original New York Times chart, or just examine a single aspect of the data for a specified city and year.
+What we might deem the most innovative update to the interactive version of the original chart is the flexibility and variety of viewing options that are available to the user.
+Our app allows the user to look at any of the three layers individually, or any combination of the three layers.
+This allows them to see the full graphic that resembles the original New York Times chart (as in Figure 2), or just examine a single aspect of the data for a specified city and year.
 
-In the 'Spaghetti Plot' tab the user can view average trends for a single city over multiple years in one graphic.
-This is advantagous to a user who is interested in assessing and comparing average weather trends between many years.
+![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)
+
+In the 'Spaghetti Plot' tab the user can view average trends for a single city over multiple years in one plot.
+This is advantagous to a user who is interested in assessing and comparing average weather trends for a city over many years.
 Additionally this plot includes data for the year 2017, which the single year plot does not.
-In order to show the user what average temperatures have been doing lately, we highlight the latest complete year (2016) and the current incomplete year.
+In order to show the user what average temperatures have been doing lately, we highlight the latest complete year (2016) and the current incomplete year (2017).
+
+![Screenshot of Spaghetti Plot in Shiny App](Images/spag_plot_screenshot.png)
 

### 2017-04-18 Web_Scraping_Final.Rmd

@@
 
-airport <- "KORD"
-ORD_daily <- data.frame(Links = links_all)  
-ORD_daily <- ORD_daily %>% nest() %>% 
+airport <- "KDET"
+DET_daily <- data.frame(Links = links_all)  
+DET_daily <- DET_daily %>% nest() %>% 
   mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
@@
 
-airport <- "KORD"
-ORD_ave_rec <- data.frame(Links = links_2016)  
-ORD_ave_rec <- ORD_ave_rec %>% nest() %>% 
+airport <- "KDET"
+DET_ave_rec <- data.frame(Links = links_2016)  
+DET_ave_rec <- DET_ave_rec %>% nest() %>% 
   mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
@@
 ```{r}
-head(ORD_daily)
+head(DET_daily)
 #names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-head(ORD_ave_rec)
+head(DET_ave_rec)
 #names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
-ORD_temps <- rbind(ORD_daily, ORD_ave_rec)
+DET_temps <- rbind(DET_daily, DET_ave_rec)
 
-ORD_temps <- ORD_temps %>% mutate(airport = airport)
-ORD_temps <- ORD_temps %>% mutate(city = "Chicago, IL") # change this each time
+DET_temps <- DET_temps %>% mutate(airport = airport)
+DET_temps <- DET_temps %>% mutate(city = "Detroit, MI") # change this each time
 
-ORD_temps <- ORD_temps %>% mutate(day = lubridate::day(date),
+DET_temps <- DET_temps %>% mutate(day = lubridate::day(date),
                                   month = lubridate::month(date),
@@
 ```{r}
-write.csv(ORD_temps, file = "raw-data/ORD_temps.csv")
+write.csv(DET_temps, file = "raw-data/DET_temps.csv")
 ```

### 2017-04-18 Paper.Rmd
web scraping section added

@@
 
+Our first step in recreating The New York Times interactive weather chart was scraping the data from the web.
+We decided to scrape our data from [Weather Underground](https://www.wunderground.com/).
+This site is a weather web service that provides real-time and historical weather information.
+The majority of their weather data comes from 1602 stations operating at airports across the US.
+For this project, we scraped temperature data for 10 cities in the Midwest: Chicago, Columbus, Des Moines, Detroit, Fargo, Madison, Minneapolis, Omaha, Sioux Falls, and St.
+Louis.
+
+We decided to scrape our data from Weather Underground because they supplied the necessary temperature data that we would need to recreate The New York Times chart in a refined table for multiple cities across the US.
+Along with that, the url was easy to update in a function according to year and city.
+Figure 1 is a screen shot for the webpage of Des Moines, IA for January 1, 2015.
+The url for this webpage is https://www.wunderground.com/history/airport/KDSM/2015/1/1/DailyHistory.html.
+In this url, "KDSM" indicates the Des Moines airport.
+Following that is the year, month, and date.
+These are the only segments of the url that change according to specified cities (i.e.
+airports) and days.
+
+![Screen shot of Weather Underground site for Des Moines, IA on Janurary 1, 2015](weather_underground_screenshot.png)
+
+For each city, two functions were run to scrape the data.
+The first function scraped the daily actual mean, maximum, and minimum temperatures.
+On the Weather Underground webpage, this is the *Actual* column seen in Figure 1.
+The maximum and minimum daily actual temperatures would later become the lower and upper bounds of the daily temperature layer on our graphic.
+Daily temperatures were scraped for each day starting on January 1, 1950 and ending on March 31, 2017.
+The second function scraped the historical average mean, maximum, and minimum temperatures as well as the record maximum and minimum for each day.
+The record years were also recorded with the record maximum and minimum.
+On the Weather Underground webpage, this is the *Average* and *Record* columns seen in Figure 1.
+The reason behind using two functions to scrape the data was due to efficiency.
+The historical averages and daily records only needed to be scraped for one year (366 days) while the daily actual temperatures needed to be scraped for all years (over 24,000 days).
+
+Along with the historic temperature data, our Shiny app scrapes the current temperature given by Weather Underground for a specified city.
+This app will be described in later sections.
+This tempurature then becomes a point on our final graphic.
+As an example, the current temperature for Des Moines can be scraped from https://www.wunderground.com/US/IA/Des_Moines.html.
+By changing the state and city in this url, we can scrape the current temperature for any city that Weather Underground reports.
+
+Web scraping was the most time consuming step of our project.
+It took approximately 7-8 hours to run our two functions that scrape the historical temperature data for each city.
+This is one of the main reasons why we only scraped data for 10 cities.
+If we had the time and computing power, we would like to have created our functions to input a vector of all 1602 Weather Underground airport codes and output one large data frame.
+If this were the case, we would most likely have to switch to a different software other than R.
+
 \subsection{Creating a Static Visual}

### 2017-04-18 shiny/app.R
change date from 1945 to 1950

@@ -17,7 +17,7 @@ shinyApp(
              inputPanel(selectInput("citySelect", label = "City:",
                                     choices = unique(temps$city), selected = "Des Moines, IA"),
                         sliderInput("yearSlider", label = "Year:",
-                                    min = 1945, max = 2016, step = 1, sep = "",value = 2015),
+                                    min = 1950, max = 2016, step = 1, sep = "",value = 2015),
                         
                         checkboxGroupInput("checkLayer", label = ("Data Layers:"), 
                                            choices = list("Record Values" = 1, 
@@ -287,7 +287,7 @@ shinyApp(
                               mean_max_min == "Mean Temperature") %>% 
         mutate(date_2016 = lubridate::ymd(paste("2016", month, day, sep = "-")))
       
-      base_spag <- temps_spag %>% filter(year < 2016) %>%
+      base_spag <- temps_spag %>% filter(year < 2016 & year > 1950) %>%
         ggplot(aes(x = date_2016, y = value, group = year)) + 
         geom_line(colour = "grey") + 
         theme_classic() +

### 2017-04-18 Paper.Rmd
intro

@@
 \section{Introduction}  
+In recent years, there has been an explosion in the use of interactive graphics and interactive data visualization, especially in the field of journalism.
+More and more media sources are making use of creative ways to present information to viewers that allows them to learn about the world around them.
+The ability to interact with these graphics allows for a powerful learning experience.
+The New York Times' "The Upshot" has been on the forefront of this vast field of exploration, as they not only have been presenting new and exciting static graphics for many decades in print, but have now expanded heavily into the world of user interaction.
+One of the quintissential examples of this user interaction is their ``How Much Warmer Was Your City in 2015" interactive graphic, based on the classic New York Times Weather Chart, published originally in 1979.
+As the framework for creating interactive graphics in `R` has expanded as well, statisticians and data scientists now have the ability to create some of these same powerfully interactive graphics.
+In fact, Amanda Cox of The Upshot actually uses `R` to sketch out some of her graphics before implementing them using the `d3` library.
+With the tools we have learned in Stat 585X at Iowa State, we can showcase these new abilities in `R` by scraping the weather data, recreating that quintissential chart, and creating a user-friendly interactive app using `shiny`.
 
@@
 
-![Screen shot of Weather Underground site for Des Moines, IA on Janurary 1, 2015](weather_underground_screenshot.png)
+![Screen shot of Weather Underground site for Des Moines, IA on January 1, 2015](Images/weather_underground_screenshot.png)
 
@@
 
+Finally, we added an option to add the current temperature at the corresponding airport.
+If the user should choose the option, our function scrapes the current temperature at that location in real-time and adds an annotated point for the current temperature.
+
 \subsubsection{Spaghetti Plot for Many Years}
@@
 This allows them to see the full graphic that resembles the original New York Times chart (as in Figure 2), or just examine a single aspect of the data for a specified city and year.
+We also give users the option to view the current temperature (scraped from the web in real time) at that location, in order to gain a reference for the current day and year.
 
@@
 ![Screenshot of Spaghetti Plot in Shiny App](Images/spag_plot_screenshot.png)
-
-\section{Discussion}
 

### 2017-04-18 Paper.Rmd
knit pdf

@@
 The New York Times' "The Upshot" has been on the forefront of this vast field of exploration, as they not only have been presenting new and exciting static graphics for many decades in print, but have now expanded heavily into the world of user interaction.
-One of the quintissential examples of this user interaction is their ``How Much Warmer Was Your City in 2015" interactive graphic, based on the classic New York Times Weather Chart, published originally in 1979.
+One of the quintissential examples of this user interaction is their "How Much Warmer Was Your City in 2015" interactive graphic, based on the classic New York Times Weather Chart, published originally in 1979.
+
 As the framework for creating interactive graphics in `R` has expanded as well, statisticians and data scientists now have the ability to create some of these same powerfully interactive graphics.
 In fact, Amanda Cox of The Upshot actually uses `R` to sketch out some of her graphics before implementing them using the `d3` library.
+
 With the tools we have learned in Stat 585X at Iowa State, we can showcase these new abilities in `R` by scraping the weather data, recreating that quintissential chart, and creating a user-friendly interactive app using `shiny`.

### 2017-04-18 Paper.Rmd
EDITED AF

--- 2017-04-18 Paper.Rmd
@@
 \section{Introduction}  
+In recent years, there has been an explosion in the use of interactive graphics and interactive data visualization, especially in the field of journalism.
+More and more media sources are making use of creative ways to present information to viewers that allows them to explore the world around them.
+The ability to interact with these graphics allows for a powerful learning experience.
+The New York Times' _The Upshot_ has been on the forefront of this vast field of exploration, as they not only have been presenting new and exciting static graphics for many decades in print, but have now expanded heavily into the world of user interaction.
+One of the quintissential examples of this user interaction is their "How Much Warmer Was Your City in 2015" interactive graphic, based on the classic 1979 New York Times Weather Chart.
+
+As the framework for creating interactive graphics in `R` has expanded as well, statisticians and data scientists now have the ability to create some of these same powerfully interactive graphics.
+In fact, Amanda Cox of _The Upshot_ actually uses `R` to sketch out some of her graphics before implementing them using the `d3` library.
+
+With the tools we have learned in Stat 585X, we can showcase these new abilities in `R` by scraping the weather data, recreating that quintissential chart, and creating a user-friendly interactive app using `shiny`.
 
@@
 
+\subsection{Scraping the Data}
+
+Our first step in recreating The New York Times interactive weather chart was scraping the data from the web.
+We decided to scrape our data from [_Weather Underground_](https://www.wunderground.com/), which is a website that provides real-time and historical weather information.
+The majority of their weather data comes from 1602 stations operating at airports across the US.
+For this project, we scraped temperature data for 10 cities in the Midwest: Chicago, Columbus, Des Moines, Detroit, Fargo, Madison, Minneapolis, Omaha, Sioux Falls, and St.
+Louis.
+
+We decided to scrape our data from _Weather Underground_ because they supply the necessary temperature data that we needed to recreate The New York Times chart in a refined table for multiple cities across the United States (see Figure 1).
+This particular website is advantageous because the url is easy to update in a function according to a specified year and city; for example, when scraping data for Des Moines, IA on January 1, 2015, we use 'https://www.wunderground.com/history/airport/KDSM/2015/1/1/DailyHistory.html' as our url to access the desired web page.
+In this url, we indicate the Des Moines airport with "KDSM", followed by year, month, and day.
+Thus, these are the only segments of the url that need to be changed in order to get information for a different city or date.
+
+\vspace{.25cm}
+
+![Screen shot of Weather Underground site for Des Moines, IA on January 1, 2015](Images/weather_underground_screenshot.png)
+
+\vspace{.25cm}
+
+Two functions were run to scrape the data for each city.
+The first function scraped the daily actual mean, maximum, and minimum temperatures, corresponding to the 'Actual' column in Figure 1.
+Daily temperatures were scraped for each day starting on January 1, 1950 and ending on March 31, 2017.
+The second function scraped the historical average mean, maximum, and minimum temperatures as well as the record maximum and minimum for each day of the year.
+These values correspond to the 'Average' and 'Record' columns seen in Figure 1.
+In addition to the record maximum and minimum values, the function also extracted the year those records originally occurred.
+These three different sets of minimum and maximum temperature values will each give the lower and upper bounds, respectively, for the three different layers of our graphic -- records, historical averages, and actual daily temperatures.
+
+We chose to use two separate functions to scrape the data in order to improve efficiency.
+Since the daily records and historical averages do not change across years, these values only needed to be scraped for one year (366 days) while the daily actual temperatures needed to be scraped for all years (over 24,000 days).
+We chose to scrape the record and historical average values from the most recent completed leap year (2016) because it seemed like a good idea at the time.
+
+In order to provide additional functionality to our users, we also created a function to scrape the current temperature given by _Weather Underground_ for a specified city.
+This real-time temperature value then becomes a point on our final graphic.
+As an example, the current temperature for Des Moines can be scraped from https://www.wunderground.com/US/IA/Des_Moines.html.
+By changing the state and city in this url, we can scrape the real-time temperature for any city available on _Weather Underground_.
+
+Web scraping was the most time consuming step of our project.
+While scraping data for historical averages and records for a single city takes under ten minutes, it takes approximately 7-8 hours to scrape daily temperatures for all years between 1950 and 2017 for that same city.
+Because this process is so computationally expensive, the scope of this project was limited to 10 cities.
+Choosing to limit this scope allowed us to spend precious computational power exploring new innovative ways for users to interact with the chart.
+
+\subsection{Creating a Static Visual}
+
+We began our exploration by building a static recreation of the original weather chart.
+We made this first static visual using the historic records and averages as well as daily temperatures for the city of Des Moines, IA.
+We created this chart for the year 2015 to allow for direct comparison with the 2015 data featured in the New York Times' interactive visual.
+We created the static visual as a base plot with many separate layers in anticipation of allowing users to choose which layers of the chart they are interested in viewing in concert.
+
+The base of the static plot (pictured in Step 1 of Figure 2) included the axes, theme, and legend that would remain constant regardless of which layers were placed on top.
+The theme and major gridlines were chosen to match the original chart as closely as possible and the y-axis limits were set to accommodate a large range of record temperatures for cities in the midwestern United States.
+Each of the dates on the x-axis of the base layer were plotted for the year 2016, and each of the remaining layers were plotted on top of those dates.
+Thus, once Shiny interactivity is introduced, leap day averages and records will appear even if a daily temperature is not available for the year chosen by the user.
+
+\vspace{.25cm}
+
 ```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 5, fig.cap = "The static visual at each of the individual steps, as layers were created and added to the chart."}
@@
 
-\subsection{Scraping the Data}
+\newpage
 
-Our first step in recreating The New York Times interactive weather chart was scraping the data from the web.
-We decided to scrape our data from [Weather Underground](https://www.wunderground.com/).
-This site is a weather web service that provides real-time and historical weather information.
-The majority of their weather data comes from 1602 stations operating at airports across the US.
-For this project, we scraped temperature data for 10 cities in the Midwest: Chicago, Columbus, Des Moines, Detroit, Fargo, Madison, Minneapolis, Omaha, Sioux Falls, and St.
-Louis.
-
-We decided to scrape our data from Weather Underground because they supplied the necessary temperature data that we would need to recreate The New York Times chart in a refined table for multiple cities across the US.
-Along with that, the url was easy to update in a function according to year and city.
-Figure 1 is a screen shot for the webpage of Des Moines, IA for January 1, 2015.
-The url for this webpage is https://www.wunderground.com/history/airport/KDSM/2015/1/1/DailyHistory.html.
-In this url, "KDSM" indicates the Des Moines airport.
-Following that is the year, month, and date.
-These are the only segments of the url that change according to specified cities (i.e.
-airports) and days.
-
-![Screen shot of Weather Underground site for Des Moines, IA on Janurary 1, 2015](weather_underground_screenshot.png)
-
-For each city, two functions were run to scrape the data.
-The first function scraped the daily actual mean, maximum, and minimum temperatures.
-On the Weather Underground webpage, this is the *Actual* column seen in Figure 1.
-The maximum and minimum daily actual temperatures would later become the lower and upper bounds of the daily temperature layer on our graphic.
-Daily temperatures were scraped for each day starting on January 1, 1950 and ending on March 31, 2017.
-The second function scraped the historical average mean, maximum, and minimum temperatures as well as the record maximum and minimum for each day.
-The record years were also recorded with the record maximum and minimum.
-On the Weather Underground webpage, this is the *Average* and *Record* columns seen in Figure 1.
-The reason behind using two functions to scrape the data was due to efficiency.
-The historical averages and daily records only needed to be scraped for one year (366 days) while the daily actual temperatures needed to be scraped for all years (over 24,000 days).
-
-Along with the historic temperature data, our Shiny app scrapes the current temperature given by Weather Underground for a specified city.
-This app will be described in later sections.
-This tempurature then becomes a point on our final graphic.
-As an example, the current temperature for Des Moines can be scraped from https://www.wunderground.com/US/IA/Des_Moines.html.
-By changing the state and city in this url, we can scrape the current temperature for any city that Weather Underground reports.
-
-Web scraping was the most time consuming step of our project.
-It took approximately 7-8 hours to run our two functions that scrape the historical temperature data for each city.
-This is one of the main reasons why we only scraped data for 10 cities.
-If we had the time and computing power, we would like to have created our functions to input a vector of all 1602 Weather Underground airport codes and output one large data frame.
-If this were the case, we would most likely have to switch to a different software other than R.
-
-\subsection{Creating a Static Visual}
-
-After data collection we were able to begin building our static recreation of the New York Times weather chart.
-We made this first static visual using the historic records, averages, and daily temperatures for the city of Des Moines, IA.
-We created this chart for the year 2015 because at the time the New York Times had a 2015 weather chart for various cities available on their website and we were able to compare our results directly.
-In anticipation of the flexiblilty that would be required to allow future users to choose a combination of layers to be plotted in a Shiny app, we created the static visual as a base plot with many layers that could be easily placed together to produce many variations of the original chart.
-
-The base of the plot included the axes, theme, and legend that would remain constant regardless of which layers were placed on top.
-The theme and major gridlines were chosen to match the orignal chart as closely as possible and the y-axis limits were set to accomodate a large range of record temperatures for midwestern cities.
-Each of the dates on the x-axis of the base layer were plotted for the year 2016 because it includes a leap year and all historic averages and records were scraped from the most recent completed year (2016).
-Thus, regardless of which year the user may choose to plot, leap day averages and records will appear even if a daily temperature is not available.
-
-The remainder of the chart was simply built by creating three layers containing seperate visuals of the historic records, averages, and daily temperatures and adding these visuals as layers to the base plot in a particular order.
-The first layer to be added to the base of the chart was for the historic records.
-This layer was created by graphing bars that spanned from the record low temperature to the record high temperature for each day over the course of one year.
-A matching legend was added to the layer and would show up whenever the layer was present on the plot.
-The next layer was constructed using bars, this time spanning from the average low to the average high temperature for each calendar day, averaged accross all years.
-This layer also included its own matching portion of legend that would plot whenever this layer was present.
-The final layer was created in a similar fashion to include boxes spanning from the daily high and low temperatures for each calendar day in 2015.
-This was the top layer and added the final data visual to the plot as well as the final piece of the legend.
-Along with this layer we also added faint white y-axis gridlines underneath it that would cross over the previous two layers and act as a reference point for viewers.
+The remainder of the chart was simply built by creating three layers containing seperate visuals of the historic records and averages as well as daily temperatures and adding these visuals as layers to the base plot in a particular order (pictured in Steps 2-4 of Figure 2).
+The first layer of data added to the base of the chart was the historic records.
+This layer was created by graphing bars that spanned from the record low temperature to the record high temperature for each day of the year.
+A matching legend was added to the layer as a description of what the bars represent.
+The next layer was constructed using bars, this time spanning from the historically averaged low to the historically averaged high temperature for each day.
+With this layer, an addition was made to the legend to explain the new set of values.
+The final layer was created in a similar fashion to include bars spanning from the daily high and low temperatures for each day in 2015.
+This top layer added the final element of the original graphic, along with a legend explaining the meaning of the layer.
+We also added faint white y-axis gridlines underneath this top layer that would cross over the previous two layers and act as a reference point for viewers.
 
@@
 
-The New York Times weather chart allows users to select a city from a drop down menu and view dail temperatures for the year 2015 along with recoreds and averages.
-We wanted to keep this useful peice of interactivity and so our users can too chose a city to view from a drop down menu.
-As already discussed in the scraping section, we have a limited scope of cities.
-When a user choses one of the midwestern cities from the menu, the data is filtered to include temperatures for that city only.
+The New York Times' interactive version of the chart allows users to select a city from a drop down menu and view daily temperatures for the year 2015 along with records and averages.
+In spite of our previously discussed limited scope of cities, we wanted to keep this element of interactivity available to users of our app.
+When a user chooses one of the midwestern cities from the menu, the data is filtered to include temperatures for that city only.
 
-Next, we wanted to implement an interactive option that wasn't available on the NYT weather chart.
-We thought that by allowing users to view daily temperatures for a large range of years, not just for 2015 would be a large improvement.
+With this original interactivity implemented, we next explored an interactive option that was not available on the New York Times web graphic.
+In the spirit of investigating historical weather trends, we decided users would find inclusion of data for multiple years valuable.
 Some of the cities that we scraped data for have daily temperature data ranging all the way back to 1945, but unfortunately the full set of cities we are working with do not agree on this start date.
@@
 
-When users select a single year, they are dictating the set of daily temperatures that will be filtered from the data and plotted in the top layer of the graphic.
-It is important to note that the record and historical averages layers will not change for any given city, no matter which year is selected.
-These are record values that are current through March 2017, either averaged with data from the current year (for average data), or updated when a record temperature occurs.
+![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)
 
-Additionally, we decided to allow the user to select which layers of the visual they would like to view together.
-The base layer and gridlines will remain constant, and as users check boxes to select which layers they want to examine, the layers are added or removed from this base plot accordingly.
-No matter which order the boxes are checked in, layers will always be added in the order they are meant to be in the original chart (i.e., records on the bottom, then averages, and finally the daily temperatures on top).
-This interactivity was made possible by a reactive function that creates seven plots of each possible layer combination for the city-year pair, and returns the one that matches the boxes that the user has checked.
+\newpage
+
+When users select a single year, they are governing the filter statement which updates the set of daily temperatures to be plotted in the top layer of the graphic.
+Users can also govern which combination of layers they would like to view together.
+The base layer and gridlines remain constant, and as users check boxes to select layers, they are added or removed from this base plot accordingly.
+No matter which order the boxes are checked in, layers will always be added in the order in which they appear on the original chart (i.e., records on the bottom, then averages, and finally the daily temperatures on top).
+This interactivity is made possible by a reactive function that creates seven plots of each possible layer combination for the city-year pair, and returns the plot that matches the chosen set of boxes.
+Finally, users are given the option to add the current temperature at the selected city.
+If the user should choose this option, our function scrapes the current temperature at that location in real-time and adds an annotated point on the appropriate month and day.
 
@@
 While the original chart recreation in the 'Single Year' tab is very informative and flexible, it only allows users to inspect a single year at a time.
-We thought it would be nice if the user could compare temperature data for a single city over many years in one place so we created a spaghetti plot feature that resides in the 'Spaghetti Plot' tab of the Shiny app.
+In order for users to compare temperature data for a single city over many years simultaneously, we created an additional interactive plot in the form of a spaghetti plot.
+This feature resides in the 'Spaghetti Plot' tab of the Shiny app.
+
+\vspace{.25cm}
+
+![Screenshot of Spaghetti Plot in Shiny App](Images/spag_plot_screenshot.png)
+
+\vspace{.25cm}
 
 Again, users are able to choose a city to investigate from a drop down menu.
-For the chosen city, the spaghetti plot is constructed with temperatures on the y-axis and month-day on the x-axis.
-Data is added to the chart by plotting a line through the average daily temperatures over the course of one year for each year.
-Lines for the years 1950 through 2015 are grey while the lines for 2016 and 2017 are colored so that the user is able to quickly see recent weather patterns and how they relate to previous years for a single city.
+For the chosen city, the spaghetti plot is constructed with temperatures on the y-axis and day of the year on the x-axis.
+A line for each year in the data set is added to the chart by connecting the average daily temperatures for one calendar year.
+Lines for the years 1950 through 2015 are plotted in grey while the lines for 2016 and 2017 are shown in color so that the user is able to quickly see recent weather patterns and how they compare to previous years for a single city.
 
@@
 
-In the 'Single Year' tab of the Shiny app, users can interact with our recreation of the original chart (see Figure 2).
-Although we have a much smaller set of cities in our Shiny app we wanted to include much of the same interactivity that the New York Times implemented, and extend to add a few new ways that users could interact with the data.
-
-The largest and most straight forward update that we wanted to include was the ability for users to choose which year to display daily temperatures for.
-The original graphic has many other impressive details, but the ability to view temperatures for a range of years will be a great advantage when investigating how weather trends change.
-Users of the app can select which year they want to look at by moving a slider input across a variety of years and the app reacts accordinly to change the top layer to reflect current temperatures for the chosen year.
-
-What we might deem the most innovative update to the interactive version of the original chart is the flexibility and variety of viewing options that are available to the user.
+With these newly implemented interactive abilities, users now have a variety of viewing options.
 Our app allows the user to look at any of the three layers individually, or any combination of the three layers.
-This allows them to see the full graphic that resembles the original New York Times chart (as in Figure 2), or just examine a single aspect of the data for a specified city and year.
-
-![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)
-
-In the 'Spaghetti Plot' tab the user can view average trends for a single city over multiple years in one plot.
-This is advantagous to a user who is interested in assessing and comparing average weather trends for a city over many years.
-Additionally this plot includes data for the year 2017, which the single year plot does not.
-In order to show the user what average temperatures have been doing lately, we highlight the latest complete year (2016) and the current incomplete year (2017).
-
-![Screenshot of Spaghetti Plot in Shiny App](Images/spag_plot_screenshot.png)
-
-\section{Discussion}
+This gives the choice between viewing the full graphic that resembles the original New York Times chart (as in Figure 2), or examining a single aspect of the data for a specified city and year.
+Because users also have the option to view the current temperature (scraped from the web in real time) at that location, they can directly compare today's temperature to weather data going back more than 60 years.
+With all of these options, we have created a powerful tool that opens a gateway for discussion about how the world is changing.
+It also enables users to begin thinking about what we really mean when we talk about weather trends, and the inherent variability that exists in weather data.
+While averages help simplify and more easily communicate complicated data, they alone lack the detail necessary to explain the changing world around us.
+In particular, the spaghetti plot shows how volatile temperatures in a single year can be, even though the plot is already comparing day-to-day averages.
+Highlighting the path that 2016 followed and the path we are 'on track' for in 2017 shows us that it is difficult to infer anything concrete when you have so much variability.
 
@@
 
-Although we believe this project has allowed us to successfully recreate an iconic weather chart and implement new interactive elements, there are still many improvements that could be made to this project.
+Although we believe this project has allowed us to successfully recreate an iconic weather chart and implement new interactive elements, there are still many improvements that could be made.
 There are several elements of the New York Times interactive graphic that we did not include in ours; the cumulative precipitation chart for each month, the average temperature for the year and how it compares to historic averages, and the ability to switch the scale to Celsius instead of Fahrenheit.
 
-Although it would require a lot of extra time to scrape precipitation data, we believe this would be a useful addition to the chart if time allowed.
-The Weather Underground does not include snow in their precipitation totals, so we would have to also take that into consideration when adding that new element to the chart, especially since our current cities are all in regions that have snowfall each winter.
+In spite of the computational roadblocks, we believe adding precipitation data would be a useful addition to the chart if time allowed.
+_Weather Underground_ does not include snow in their precipitation totals, so we would need to consider this situation when adding this element to the chart, especially given our current focus on the Midwest.
 
-In the top left corner of the original graphic, there is a note about what the year's average temperature was in that city, and how much higher or lower that overall average was than the historic average.
-As that was the focus of their chart on the interactive chart page, ``How Much Warmer Was Your City in 2015", it is difficult for statisticians to reconcile one overall average temperature for the entire year without any further explanation, especially for cities in which winter temperatures greatly vary from summer temperatures.
-We would like to explore other options to communicate this information, and perhaps find a more accurate or detailed way to display it to viewers.
+In the top left corner of the original graphic, there is a note about what the year's average temperature was in the chosen city, and how much higher or lower that overall average was than the historic average.
+As that was the focus of their chart on the interactive chart page, "How Much Warmer Was Your City in 2015", it is difficult for statisticians to reconcile one overall average temperature for the entire year without any further explanation.
+This becomes increasingly important when considering cities in which winter temperatures greatly vary from summer temperatures.
+We would like to explore other options to communicate this information and perhaps find a more accurate or detailed way to display it to users.
 
-Although it would simply require a change in the axes and a transformation of the data, we did not create the option for users to change between Celsius and Fahrenheit.
-With all the other options available to users, it would be a bit clunky to also add in that transformation.
+We did not create the option for users to change between Celsius and Fahrenheit.
+With the way the app is currently constructed, this change would significantly lengthen the time between user choice and rendering of the plot.
 
-The biggest roadblock for a lot of these issues is the code that we are working with.
-Scraping the data takes quite a while, because we have to open a link separately for each day we want data for in history.
-However, if we could find a quicker way to scrape this data, we would be very interested in expanding the scope of cities we have data for so that users have even more to work with.
-The framework we have set up for the Shiny interactivity also means that a lot of things have to happen to our data inside the app itself before we can display the image that the user would like to see; once we filter the data by city and year, the graphics themselves have to be created and then displayed based on which layers the user is interested in.
-If we could find a way to render much of this information outside of the 'reactive' statement or a better way to do it in general, we would be able to have more options and they would render more quickly.
+The biggest roadblock for a lot of these issues is the structure with which we are working.
+As discussed in Section 2.1, scraping the data is extremely time consuming.
+However, if we could find a quicker way to scrape this data, we would be very interested in expanding the scope of cities beyond the current set so that users have even more to work with.
+The framework we have set up for the Shiny interactivity also means that a lot of things have to happen to our data inside the app itself before we can display the image that the user would like to see.
+Once we filter the data by city and year, the graphics themselves have to be created and then displayed based on which layers the user is interested in.
+If we could find a way to render much of this information outside of the 'reactive' statement or create a more efficient structure for this process, we would be able to render plots more quickly and thus implement more interactivity options.
 
-Finally, we would like to be able to add some interactivity with the `plotly` package, or at least be able to denote record temperatures that happen in a given year when they occur.
-The original chart denotes when record values happen and labels them with what the value of that record temperature was.
-If we could allow users to be able to scroll over the values for the current year, they could see what the actual values were that make up the different layers.
-However, as it stands at the moment, when `plotly` is added to the graphic, it is extremely slow and takes approximately 1 minute to render a single plot.
+Finally, we would like the ability to add some interactivity with the `plotly` package, or at least be able to denote record temperatures that occur during the chosen year.
+The original chart denotes when record values happen and labels them with the value of that record temperature.
+If we could allow users to be able to scroll over the values for the current year, they could see the actual values that make up each of the different layers.
+As it stands, when `plotly` is added to the graphic it is extremely slow and takes approximately one minute to render a single plot.
 This is clearly an unreasonable amount of time for a user to wait for an image, especially if they want to switch around layers quickly.
 
-Although we have not created an actual R package, we believe it would be a really fun interactive environment for users to look into, as well as for professors to use as teaching material - either about `ggplot2`, `shiny`, or just about interactive graphics in general.
-It may be advantageous to have this as a full R package available at least via GitHub, and let users know what they can do with the available data and the shiny app.
+At this point in time, we have not created an actual R package.
+However, we believe it would be a really fun interactive environment for users to look into.
+In addition, professors could make use of the data and the full app as teaching material -- either about `ggplot2`, `shiny`, time series data, or just about interactive graphics in general.
+It may be advantageous to have this as a full R package, available at least via GitHub, with documentation to explain how users can access the full functionality of the scraped data and app.

### 2017-04-18 Paper.Rmd
fixed position on fig 3
Fixing figure 3, attempt 2

@@
 
-![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)
+```{r, fig.height = 3, fig.width = 12, warning = F, message = F, echo = F, fig.cap = "Screenshot of Single Year Tab in Shiny App"}
+library(png)
+library(grid)
+img <- readPNG("Images/single_year_screenshot.png")
+grid.raster(img)
+```
 

### 2017-04-24 shiny/app.R
app updates

@@ -256,12 +256,12 @@ shinyApp(
         cur_point_legend <-  annotate("text",
                                       label = paste0("Current Temperature in ", input$citySelect), 
                                       x =  cur_date, 
-                                      y = cur_temp + 25, 
+                                      y = 110, 
                                       hjust = "left", 
                                       size = 3)
         cur_point_legend_line <- geom_segment(aes(x = cur_date,
                                                  xend = cur_date,
-                                                 y = cur_temp + 23,
+                                                 y = 110,
                                                  yend = cur_temp + 2),
                                               size = 0.05, arrow = arrow(length = unit(0.3,"cm")))
         display_plot <- display_plot + cur_point_layer + cur_point_legend + cur_point_legend_line
@@ -303,7 +303,7 @@ shinyApp(
         xlab("") +
         ylab("")
       
-      layer_2016 <- geom_line(data = temps_spag[temps_spag$year == 2016,], aes(x = date_2016, y = value), colour = "maroon")
+      layer_2016 <- geom_line(data = temps_spag[temps_spag$year == 2016,], aes(x = date_2016, y = value), colour = "steelblue")
    
       layer_2017 <- geom_line(data = temps_spag[temps_spag$year == 2017,], aes(x = date_2016, y = value), colour = "steelblue", lwd = 1.5)
       
@@ -317,7 +317,7 @@ shinyApp(
                                          xmax =  lubridate::ymd("2016-07-27"), 
                                          ymin = -9, 
                                          ymax = -8.5), 
-                                     fill = "maroon")
+                                     fill = "steelblue")
       
       legend_layer_blue <- geom_rect(aes(xmin = lubridate::ymd("2016-07-13"), 
                                          xmax =  lubridate::ymd("2016-07-27"), 

### 2017-04-24 shiny/app.R
changing label

@@ -108,7 +108,7 @@ shinyApp(
                                         fill = "#BCACAC", alpha = 0.8)
       
       text_layer_average <-  annotate("text",
-                                      label = "Normal range", 
+                                      label = "Range of Historical Averages", 
                                       x =  lubridate::ymd("2016-07-19"), 
                                       y = 0, 
                                       hjust = "right", 

### 2017-04-25 Paper.Rmd
image things
changing legends

--- 2017-04-18 Paper.Rmd
@@
 text_layer_average <-  annotate("text",
-                                label = "Normal range", 
+                                label = "Range of Historical Averages", 
                                 x =  lubridate::ymd("2016-07-19"), 
@@
 
-![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)
+```{r, fig.height = 3, fig.width = 12, warning = F, message = F, echo = F, fig.cap = "Screenshot of Single Year Tab in Shiny App"}
+library(png)
+library(grid)
+img <- readPNG("Images/single_year_screenshot2.png")
+grid.raster(img)
+```
 
